### 2013-12-14 paper/paper.tex
Add paper in TeX.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{Market-based Mechanisms for Resource Scheduling}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Paul Christiano
% 2nd. author
\alignauthor
Frank Li
% 3rd. author
\alignauthor
Richard Shin
%\and  % use '\and' if you need 'another row' of author names
%% 4th. author
%\alignauthor Lawrence P. Leipuner\\
%       \affaddr{Brookhaven Laboratories}\\
%       \affaddr{Brookhaven National Lab}\\
%       \affaddr{P.O. Box 5000}\\
%       \email{lleipuner@researchlabs.org}
%% 5th. author
%\alignauthor Sean Fogarty\\
%       \affaddr{NASA Ames Research Center}\\
%       \affaddr{Moffett Field}\\
%       \affaddr{California 94035}\\
%       \email{fogartys@amesres.org}
%% 6th. author
%\alignauthor Charles Palmer\\
%       \affaddr{Palmer Research Laboratories}\\
%       \affaddr{8600 Datapoint Drive}\\
%       \affaddr{San Antonio, Texas 78229}\\
%       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Large-scale computing clusters offer potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated \emph{fairness}
criterions, such as dominant resource fairness (DRF), which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings---when dealing with inhomogeneous resources, time-varying
demands, requirements for data locality, etc.---these systems cease to be either
efficient or non-manipulable.

We propose using prices as an abstraction for subsystems to communicate their
constraints, and describe a protocol based on auctions for allocating resources
in a cluster. Our protocol has the key advantage that it can continue to meet
efficiency guarantees in realistic environments where preferences are
inhomogeneous across resources and time, and in the presence of adversarial
manipulation. Moreover, we propose prices as a general mechanism for enforcing a
clean abstraction between different components of a system, allowing one
component to make choices intelligently based on constraints elsewhere in the
system even when it was not designed with knowledge of those constraints.

We implement these ideas in the Mesos cluster manager, along with microeconomic
``agents'' which allow traditional Mesos clients to interact seamlessly with our
modified implementation. We show that the computational and communication
overhead proposed by our system is manageable and that its performance compares
favorably to existing approaches (particularly DRF) even when users don’t
provide any meaningful price information. Moreover, we show that when accurate
economic data is available our system is able to achieve substantially higher
social welfare than DRF. Finally, we discuss a number of examples where this
functionality may be useful even in applications where the end-users of the
system don't have to think about economics at all, and instead prices are
generated algorithmically as a principled way to accommodate constraints that
are currently managed in an ad hoc way.
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
\subsection{Overview}
We consider an environment in which a single cluster is used for a variety of
tasks, which may have very different demands for resources. For example, a
company might run research tasks in the same cluster as production web services,
in order to make use of computational resources which would otherwise lie idle
when web traffic is low. In general, running different tasks in the same cluster
has the promise of improving utilization and reducing overhead.

Different tasks may have significantly different demands for resources; some may
have deadlines on the scale of seconds while others have deadlines of hours or
days, some may require specialized hardware available on only certain machines,
some may require using the same machines consistently while others can use
different machines at different times, some may have complex constraints on data
locality, etc.

\subsection{Mesos}
The Mesos cluster manager is designed to address these problems, and to run
several independent \emph{frameworks} on a single cluster. Its core design philosophy
is to make minimal assumptions about the behavior of the frameworks it hosts. To
this end it allocates resources using ``resource offers,'' and leaves it up to the
frameworks themselves to decide which resources they will use and which they
will pass on. Frameworks are free to make these decisions on the basis of the
detailed specifications of the tasks they want done (for example, to accept
machines that improve data locality), but Mesos itself makes use of a very
simple fairness criterion to decide which frameworks receive offers.

The abstraction of resource offers allows Mesos to serve frameworks without
understanding the constraints they face. By making offers to those frameworks
which are currently using the least resources, Mesos attempts to ensure that all
frameworks receive a fair share of the cluster. Because of the simplicity of
this protocol, it appears to be immune to manipulation (and indeed it has been
shown to be immune to manipulation in theory).

Unfortunately, while the fairness policy used by Mesos is efficient and
strategy-proof in a simple one-shot game with homogeneous resources, it is
neither efficient nor strategy-proof in this setting. For example, a framework
using Mesos which prefers to run tasks on machines that already have relevant
data is forced to engage in strategic behavior: given a resource which it
\emph{could} use now, should it take the resource or decline it, so that it
might receive a better offer in the future? Solutions to this problem rely on
simple heuristics which require tuning based on the parameters of the system;
there are simple examples where the resulting allocations are not efficient
despite best-efforts of the clients, and in complex examples there is little to
believe the results are efficient. Moreover, despite being ``strategy-proof'' the
current design of Mesos is essentially unsuitable for even mildly hostile
environments; a framework which can use less than its ``fair share'' of the
resources at any point in time has no incentive to do so, and indeed has every
incentive to exploit all resources it can be allocated even if they are being
used arbitrarily inefficiently (and there is always \emph{something} to do with
idle resources, if only perform proof-of-work in exchange for small amounts of
money).

\subsection{Microeconomic methods}
In this paper we confront the challenge of modifying Mesos to provide more
robust efficiency guarantees, without compromising its agnosticism regarding the
nature of different frameworks’ desiderata. We propose \emph{price signals} as a
mechanism for accomplishing this; instead of accepting or rejecting a resource
offer, a framework can express its preferences by assigning a \emph{willingness
to pay} for that resource, and Mesos can give the resources to whichever
frameworks are most willing to pay.

We stress the distinction between this use of price signals and the more typical
motivation. We are most interested in price signals as an \emph{abstraction} which
programs can use to express their constraints, rather than as a mechanism to
extract revenue for the cluster operator or to arbitrate between competing
external interests. To consider a simple case, suppose there are two programs
that are contending for a shared resource $R$. Each could either make use of $R$ or
some alternative resource $R'$ (for example, a different machine in the cluster at
a different time). Our proposal is to have each program articulate the value of
resource $R$ (compared to the benchmark of not receiving resource $R$, and then
contending for resource $R'$ at a later date). The primary alternatives that have
been considered are:
\begin{enumerate}
  \item Ignore the relative value of resource $R$ and $R'$, and make allocation
    decisions entirely on the basis of fairness considerations (for example by
    ensuring that each framework has an equal number of every resource). This is
    the approach taken by Mesos, although it in fact achieves better behavior
    precisely by \emph{violating} the strategy-proofness of its underlying allocation
    policy, and providing incentives to frameworks to strategically decline a
    resource in order to receive a better allocation in the future.
  \item Understand the entire optimization problem faced by each problem, and
    make explicit judgments of the relative value of $R$ and $R'$ within the
    scheduler. This violates the spirit of Mesos, and in general appears to be
    difficult given the complexity and scale of the cluster scheduling problem.
\end{enumerate}

\subsection{Guide to the paper}
In section 2, we make the theoretical case for using microeconomic methods. We
provide a litany of examples in which existing approaches, and in particular
DRF, fail to be either efficient or strategy-proof, and describe examples of
strategic behavior in Mesos. We discuss a number of examples in which economic
data generated \emph{within} the system could be useful, and compare this approach to a
number of ad hoc approaches currently pursued to solve similar problems.

In section 3, we describe our protocol and the most important design decisions
we made. In particular, we describe the mechanisms we used to ensure that our
protocol remains backwards-compatible, and can be applied without any change to
the clients’ code.

In section 4, we describe our implementation of this protocol within Mesos.

In section 5, we report on experimental comparisons between our results and
existing approaches: (a) we evaluate the computational and communication
overhead of our approach and show that it is manageable, (b) we compare our
system in ``backwards-compatibility mode,'' without any economic information
whatsoever, to DRF, and show that it performs comparably whether judged by
utilization or fairness, (c) we examine a number of cases in which economic
information is available; we show that in general our algorithms achieve higher
social efficiency than DRF, and provide natural examples in which DRF fails to
be Pareto efficient.

\section{The case for microeconomic scheduling}
\subsection{Scheduling is hard}
Consider the following typical situations within a cluster:
\begin{enumerate}
  \item Some clients have regular throughput and flexible deadlines, while some
    clients have hard real-time constraints and variable traffic.
  \item Different tasks make use of different characteristics of hardware on
    machines in the cluster, for example high ratios of RAM to CPU on a
    particular machine, or GPUs or other hardware that is available on only
    certain machines.
  \item Tasks require data which is located on disk or even in memory somewhere
    in the cluster, and co-locating the tasks with the data improves
    performance.
\end{enumerate}
In each of these examples, clients of the cluster have preferences over
allocations which are difficult to precisely express. It would be possible but
difficult to cover just these cases, but the reader can doubtless generate many
similar cases, and as the environment changes the nature of these constraints is
likely to continue to change as well.

Mesos is able to schedule even in the face of such constraints, by making
resource offers to clients and allowing them to accept or reject resources
according to whether they satisfy their constraints. But this is approach offers
little granularity to clients, forces them to adopt brittle heuristics, and
moreover compromises the guarantees of the fairness policies Mesos uses to
decide how to make resource offers.

Mesos uses a fair-share scheduler based on dominant resource fairness. This
means that the client to receive the next resource offer is the one who is
currently using the minimum share of the resource they are using the \emph{most}
of (relative to the total supply in the cluster). A weighted version can be
defined analogously.

Consider a client of Mesos who is interested in receiving a machine with
characteristic X, because it would allow their task to run 20\% faster (or
perhaps because it would allow them to run a task which is slightly higher
priority than the task they would run on a machine without characteristic X).
Given an offer for a machine without characteristic X, what should this client
do? The formal guarantee of ``strategy-proofness'' suggests the client would take
it; indeed, to do otherwise would explicitly be strategic. But in fact, we hope
that clients will yield a highly-contended resource when they can use an
alternative, or will yield a typical resource if they could make particularly
good use of an alternative. And indeed this is done by many clients to Mesos.

This example clearly shows that in this case, the mechanism provided by Mesos is
\emph{not} strategy-proof. Worse, it’s not Pareto efficient if people are
honest, and need not be Pareto efficient if clients behave optimally. Similar
things happen in the other examples we mentioned, or in most of the similar
alternatives which we can envision:
\begin{enumerate}
  \item When one client has a constant stream of work and another has varying
    traffic, Mesos encourages both to constantly use up their allocated share of
    the network (unless they have nothing to do with the space). But an
    efficient allocation would give the client with varying workload more
    resources when it has more work. 
  \item Mesos gives a valuable resource to whatever client happens to be using
    the fewest resources when that machine becomes available. This encourages
    clients to inefficiently decline resources which they could use, so that
    they will be offered better resources in the future. This may decrease
    utilization, and moreover it provides little guarantee that a valuable
    resource will be used by the framework which most values it---instead it will
    be used by whichever framework uses the least resources.
  \item If a client is waiting for a machine that is co-located with some data
    that their task needs, then Mesos encourages them to guess how likely that
    resource is to be freed up soon, and to decline new resources if this
    probability is high enough. This is actually much more efficient behavior
    than if the client behaved honestly by accepting whatever resources it could
    use, but it provides some indication that the ``guarantees'' of DRF are not
    directly applicable to the situations Mesos is intended to cover.
  \end{enumerate}

These shortcomings are not specific to DRF; these will be issues for any
scheduler which treats the scheduling problem as a one-shot game with
homogeneous resources when in fact it is more complicated. Theoretical
guarantees are not likely to be meaningful in this regime. To evaluate proposed
solutions, we suggest a combination of:
\begin{enumerate}
  \item Theoretical analyses which apply in realistic contexts
  \item Experimental evidence for effectiveness
\end{enumerate}
We provide strong evidence that our proposal is at least not inferior to DRF on
either of these grounds, and we provide some evidence that even our highly
preliminary implementation is already superior.

\subsection{Existing approaches}
Many difficulties with scheduling have been isolated and addressed, typically by
ad hoc mechanisms which require tuning and don't necessarily play nicely with
each other. In order to contrast these approaches with microeconomic methods, we
list some examples of solutions to these problems here. Note that we will not be
able to solve all of these problems within our proposal---that would be an
extraordinarily ambitious project. We list these examples to give some sense of
how a microeconomic framework could be used to replace ad hoc approaches,
improving robustness and ease-of-design. In contrast, our goal in this paper is
simply to show that microeconomic approaches really are a feasible option, and
that in the ``base case'' they are as good as existing solutions.

\paragraph{Deadlines} DRF makes no provision for coping with deadlines, which
are often of considerable practical importance. The Jockey system enforces
deadlines in the context of a fair-share scheduler, by increasing or decreasing
a task's share of the cluster depending on the importance of their deadline.
While this is a significant improvement over the alternative, we find it a very
crude solution to the underlying problem:
\begin{enumerate}
  \item Jockey has no dependence on how important resources currently are for
    the cluster, it just assigns a job as many resources as are needed to meet
    its deadline.
  \item It is not clear how to generalize Jockey to systems where multiple
    simultaneous tasks have deadlines, or where meeting deadlines must be
    balanced against any other consideration.
  \item Jockey changes the allocations of tasks depending on their performance,
    and will typically invalidate any guarantees provided by the original
    scheduler.
  \item Jockey does not have any principled approach for reasoning about the
    error bars on a task's completion time (instead this is determined by a
    fine-tuned parameter of the system).
  \item Jockey cannot reason about multiple deadlines of varying importance, but
    instead gives a job as many resources as it needs to finish as soon as it
    would be useful.
\end{enumerate}

The microeconomic alternative makes use of Jockey's core component, an estimate
for the time required to complete a task, but uses a different control system.
In the microeconomic framework a deadline is associated with an economic value
(that might be algorithmically generated based on the priority of the task)
which can be compared to the economic value of other activity in the cluster.
The importance of resources to the task is then given by the effect those
resources will have on the task's probability of completing by deadline, and
this can be compared to the importance of those resources to other processes
running on the cluster. Resources can then be shifted until these two values are
equal.

\paragraph{Priority and preemption} In existing systems priority is typically
implemented as an absolute ordering; a task of high priority can preempt a task
of lower priority and always wins in contention for resources. This approach is
conceptually problematic because there are always mechanisms for a
higher-priority process to improve performance by increasing its resource usage
(for example speculative execution, or increased duplication of straggling
processes) and an infinite tradeoff between the performance of high-priority and
low-priority processes is undesirable. In practice, this approach relies on
``reasonable'' behavior by high-priority processes, which makes reasoning about
systems difficult. Such systems are also brittle and prone to priority
inversions, in which low-priority processes can be inadvertently elevated to
high-priority.

Another approach is to assign tasks of different types appropriate shares of a
cluster. But this approach also fails to capture what we really care about. For
example, we would like high priority processes to expand their use of the
cluster when they need it.

These problems are considerably exacerbated when we consider preemption,
especially if preemption is costly for the preempted process: when should a low
priority process be allowed to finish, and when should it be preempted?

Microeconomic methods allow for a principled answer to these questions: by
describing ``high priority'' tasks by \emph{how much more} we care about them
finishing faster, we can make principled tradeoffs.

\paragraph{Data locality} Many tasks run more efficiently when they are
co-located with data. At the moment, this is typically achieved either by
explicit optimization (requiring the scheduler to be aware of detailed
characteristics of the tasks its scheduling) or by heuristics, for example
blocking for 5 seconds before accepting an offered resource which is not local
to data. Again, microeconomic methods provide a principled approach which is
compatible with a lightweight interface between client and scheduler: a client
can estimate how much more slowly a task will run on a machine without the data,
can estimate how likely a machine with the data is to become free, and can
thereby estimate how much of a discount they would need to be offered before
they would accept a machine without their data.

\subsection{Philosophical motivation}
Our primary motivation is strongly to maximize efficiency, rather than other
measures such as utilization, fairness, or strategy-proofness. We view other
characteristics as necessary insofar as they help achieve efficiency.

In some sense this is problematic, because efficiency is typically unmeasurable.
But there are a number of pragmatically relevant implications:
\begin{enumerate}
  \item Pareto efficiency is a minimal standard for acceptability. To the extent
    that existing approaches fail to be Pareto efficient, this is much more
    damning than a possible failure to be strategy-proof (as long as the
    possibility of manipulation does not in itself destroy our efficiency
    guarantee!)
  \item Even where true prices are unavailable, we think in terms of the real,
    unobserved value of an outcome (such as finishing a computation or meeting a
    deadline). Many existing schemes need to implicitly make judgments about
    these values (because they are making tradeoffs between different outcomes).
    So we don't treat the difficulty of assigning values to outcomes as a
    deal-breaker; to the extent that we already need to make implicit tradeoffs,
    reifying those tradeoffs is only likely to help us improve the situation.
\end{enumerate}

\subsection{Why microeconomic methods?}
The basic paradigm we propose is conceptually simple, though is associated with
many practical difficulties. At each stage where we need to make a decision, we
propose:
\begin{enumerate}
  \item Estimate the value of different outcomes.
  \item Estimate the outcomes that will result from different decisions.
  \item Compute the value of different decisions.
\end{enumerate}

This paradigm has the virtue of being modular in a number of important respects:
\begin{enumerate}
  \item The notion of value provides a unifying framework for different
    components to communicate with each other; if I am one component providing a
    service to some client, and I know how valuable different outcomes are to my
    client, I know everything I need to know; my policy does not need to depend
    on anything else about the client.
  \item I can improve and reason about the prediction of outcomes and the
    estimates of value separately. 
  \item It is often possible to compute the value straightforwardly, given the
    values stated  by my clients. For example, if I am scheduling a MapReduce
    instance and know that a 1 second delay costs my client 1 unit, then I can
    estimate the cost of a 1 second delay in one of my tasks simply by
    estimating (or using a crude heuristic for) the probability that this task
    is on the critical path.
\end{enumerate}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%% This next section command marks the start of
%% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The acm\_proc\_article-sp document class file itself is chock-full of succinct
%and helpful comments.  If you consider yourself a moderately
%experienced to expert user of \LaTeX, you may find reading
%it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

### 2013-12-14 paper/paper.tex
Organization/formating fixes

@@
 
-\numberofauthors{3} %  in this sample file, there are a *total*
+\numberofauthors{1} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 % 1st. author
-\alignauthor
-Paul Christiano
+\alignauthor Paul Christiano, Frank Li, Richard Shin \\
 % 2nd. author
-\alignauthor
-Frank Li
 % 3rd. author
-\alignauthor
-Richard Shin
+\email{\{paulchristiano, frankli, ricshin\}@cs.berkeley.edu}
 %\and  % use '\and' if you need 'another row' of author names
@@
 \begin{abstract}
+
+\end{abstract}
+
+% A category with the (minimum) three required fields
+%\category{H.4}{Information Systems Applications}{Miscellaneous}
+%A category including the fourth, optional field follows...
+%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+
+%\terms{Theory}
+
+%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+
+\section{Introduction}
+\label{sec:intro}
+
 Large-scale computing clusters offer potential for greater efficiency through
@@
 overhead proposed by our system is manageable and that its performance compares
-favorably to existing approaches (particularly DRF) even when users don’t
+favorably to existing approaches (particularly DRF) even when users do not
 provide any meaningful price information. Moreover, we show that when accurate
@@
 are currently managed in an ad hoc way.
-\end{abstract}
 
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+\subsection{Guide to the paper}
 
-%\terms{Theory}
+In section \ref{sec:overview}, we provide a brief overview of Mesos and how it
+could incorporate microeconomic mechanisms.
 
-%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+In section \ref{sec:case}, we make the theoretical case for using microeconomic methods. We
+provide a litany of examples in which existing approaches, and in particular
+DRF, fail to be either efficient or strategy-proof, and describe examples of
+strategic behavior in Mesos. We discuss a number of examples in which economic
+data generated \emph{within} the system could be useful, and compare this approach to a
+number of ad hoc approaches currently pursued to solve similar problems.
 
-\section{Introduction}
-\subsection{Overview}
+In section \ref{sec:design}, we describe our protocol and the most important design decisions
+we made. In particular, we describe the mechanisms we used to ensure that our
+protocol remains backwards-compatible, and can be applied without any change to
+the clients’ code.
+
+In section \ref{sec:eval}, we report on simulated comparisons between our
+design and existing approaches: (a) we evaluate the computational and communication
+overhead of our approach and show that it is manageable, (b) we compare our
+system in ``backwards-compatibility mode,'' without any economic information
+whatsoever, to DRF, and show that it performs comparably whether judged by
+utilization or fairness, (c) we examine a number of cases in which economic
+information is available; we show that in general our algorithms achieve higher
+social efficiency than DRF, and provide natural examples in which DRF fails to
+be Pareto efficient.
+
+\section{Overview}
+\label{sec:overview}
+
 We consider an environment in which a single cluster is used for a variety of
@@
 robust efficiency guarantees, without compromising its agnosticism regarding the
-nature of different frameworks’ desiderata. We propose \emph{price signals} as a
+nature of different frameworks' desiderata. We propose \emph{price signals} as a
 mechanism for accomplishing this; instead of accepting or rejecting a resource
@@
 
-\subsection{Guide to the paper}
-In section 2, we make the theoretical case for using microeconomic methods. We
-provide a litany of examples in which existing approaches, and in particular
-DRF, fail to be either efficient or strategy-proof, and describe examples of
-strategic behavior in Mesos. We discuss a number of examples in which economic
-data generated \emph{within} the system could be useful, and compare this approach to a
-number of ad hoc approaches currently pursued to solve similar problems.
+\section{The case for microeconomic scheduling}
+\label{sec:case}
 
-In section 3, we describe our protocol and the most important design decisions
-we made. In particular, we describe the mechanisms we used to ensure that our
-protocol remains backwards-compatible, and can be applied without any change to
-the clients’ code.
-
-In section 4, we describe our implementation of this protocol within Mesos.
-
-In section 5, we report on experimental comparisons between our results and
-existing approaches: (a) we evaluate the computational and communication
-overhead of our approach and show that it is manageable, (b) we compare our
-system in ``backwards-compatibility mode,'' without any economic information
-whatsoever, to DRF, and show that it performs comparably whether judged by
-utilization or fairness, (c) we examine a number of cases in which economic
-information is available; we show that in general our algorithms achieve higher
-social efficiency than DRF, and provide natural examples in which DRF fails to
-be Pareto efficient.
-
-\section{The case for microeconomic scheduling}
 \subsection{Scheduling is hard}
@@
 
+\section{Market-based Mechanism Design}
+\label{sec:design}
+
+\section{Evaluation}
+\label{sec:eval}
+
+\section{Future Works}
+\label{sec:future}
+
+\section{Conclusion}
+\label{sec:conclusion}
 %

### 2013-12-14 mesosSim.cpp

@@ -106,7 +106,6 @@ class MesosSimulation : public Simulation<MesosSimulation> {
   Indexer<Job> allJobs;
 
   size_t round_robin_next_framework;
-  unordered_map<size_t, int> framework_num_tasks_available;
   // A mapping from jobs to the IDs of the tasks which depend on these jobs.
   unordered_multimap<size_t, size_t> job_dependents;
 
@@ -176,6 +175,8 @@ void trace_workload(
 
   allJobs.add(0); // Dummy job with 0 tasks so that real jobs begin at ID 1.
 
+  unordered_map<size_t, double> framework_join_time;
+
   string line;
   ifstream trace(FLAGS_trace);
   CHECK(trace.is_open()) << FLAGS_trace << " not opened";
@@ -198,6 +199,14 @@ void trace_workload(
     task.task_time = split_v[3] - split_v[2];
     task.start_time = split_v[2];
     task.special_resource_speedup = split_v[10];
+
+    if(framework_join_time.count(task.framework_id) == 0) {
+      framework_join_time[task.framework_id] = task.start_time;
+    } else if (framework_join_time.count(task.framework_id) > 0) {
+      framework_join_time[task.framework_id] = min( framework_join_time[task.framework_id], task.start_time);
+    }
+    assert(framework_join_time.count(task.framework_id) > 0);
+
     // Add dependencies of task
     for(int i = 11; i < split_v.size(); i++) {
       CHECK_NE(split_v[i], task.job_id) << "Self-dependency not allowed";
@@ -235,6 +244,10 @@ void trace_workload(
       job->start_time = task.start_time;
     }
   }
+  for(auto& kv : framework_join_time) {
+    sim->add_event(new OfferEvent(framework_join_time[kv.first] + 1));
+  }
+
   trace.close();
 }
 
@@ -348,14 +361,6 @@ void MesosSimulation::start_task(
       f.cpu_share, f.mem_share, f.disk_share
     });
 
-    CHECK_GT(framework_num_tasks_available.count(f.id()), 0);
-    framework_num_tasks_available[f.id()] -= 1;
-    CHECK_GE(framework_num_tasks_available[f.id()], 0);
-    if (framework_num_tasks_available[f.id()] == 0) {
-      framework_num_tasks_available.erase(f.id());
-      CHECK_EQ(framework_num_tasks_available.count(f.id()), 0);
-    }
-   
     double task_runtime = task.task_time;
     if (slave.special_resource) task_runtime *= task.special_resource_speedup;	
[…]

### 2013-12-14 plot.py

@@ -5,12 +5,21 @@ import sys
 print(sys.argv)
 drf = np.loadtxt(sys.argv[1])
 auction = np.loadtxt(sys.argv[2])
+roundrobin = np.loadtxt(sys.argv[3])
+
+fig,ax = plt.subplots()
+ax.yaxis.grid(b=True, which='both')
+ax.set_xticks(range(50))
+ax.xaxis.grid(b=True, which='both')
+
 plt.xlabel("time (in hours)")
 plt.ylabel("CPU utilization")
 plt.title("CPU utilization")
-plt.axis([0,180000/3600,0,1])
+plt.axis([0,90000/3600,0,1])
 plt.plot(drf[:,0]/3600.0, drf[:,1]/drf[:,2], label="DRF")
 plt.plot(auction[:,0]/3600.0, auction[:,1]/auction[:,2], label="Auction")
+plt.plot(roundrobin[:,0]/3600.0, roundrobin[:,1]/roundrobin[:,2], label="Round Robin")
+
 plt.legend(loc="center right") 
 plt.show()
 
@@ -22,8 +31,9 @@ ax.xaxis.grid(b=True, which='both')
 plt.xlabel("time (in hours)")
 plt.ylabel("Memory utilization")
 plt.title("Memory utilization")
-plt.axis([0,180000/3600,0,1])
+plt.axis([0,90000/3600,0,1])
 plt.plot(drf[:,0]/3600.0, drf[:,3]/drf[:,4], label="DRF")
 plt.plot(auction[:,0]/3600.0, auction[:,3]/auction[:,4], label="Auction")
+plt.plot(roundrobin[:,0]/3600.0, roundrobin[:,3]/roundrobin[:,4], label="Round Robin")
 plt.legend(loc="center right") 
 plt.show()

### 2013-12-16 paper/paper.tex
More org changes
Adding first part of evaluation (1 page)

@@
 be Pareto efficient.
+
+In section \ref{sec:future}, we elaborate on directions for further
+investigation.
+
+In section \ref{sec:conclusion}, we making closing remarks.
 
@@
 
-\section{Evaluation}
+\section{Experimental Evaluation}
 \label{sec:eval}
+
+To evaluate the performance of the market-based mechanism compared with DRF,
+we implemented an event-based simulation of Mesos with both resource scheduling algorithms.
+We study the performance of DRF and the market-based mechanism both when pricing information is not available and a default bidding policy must be used, and when pricing information is specified under a specific policy.
+These simulations were run under a statistical workload generated from a month-long Google cluster trace \cite{TODO}.
+
+\subsection{Simulation Implementation\\}
+
+Our evaluation is conducted through an event-based simulator of Mesos, implemented with both the DRF and the auction-based resource scheduling algorithms.
+We chose to use simulations because it allowed for simplified evaluation over a variety of environmental variables, such as the number of nodes in the cluster or resources per node, and provided an efficient method for testing various bidding policies.
+Our simulator was implemented in C++ using approximately 1200 lines of code.
+
+The simulations were run on synthetic workloads generated from the statistical distributions of a month-long Google cluster trace.
+The Google traces, captured during May 2011, identify cluster jobs as well as the tasks that compose each job.
+For each task that finishes successfully (without failing or being terminated), we extract the start and finish times, priority information, and normalized resource requests for CPU cores, RAM, and local disk space.
+The traces indicated that jobs were heavily CPU-bound.
+We assume tasks run under the amount of resources requested and the task execution times are simply the differences between the finish and start times.
+We generate workloads that follows the same statistical distribution as this extracted data.
+The benefit of this statistical workload approach is that we can generate various synthetic workloads that model a real-world workload.
+
+\subsection{Performance Without Pricing\\}
+
+Currently, Mesos jobs and tasks are not attached to economic indicators, since DRF does not rely on any economic-based resource scheduler.
+Even if a market-based mechanism was used, many cluster jobs and tasks may not be able or willing to provide accurate pricing data.
+In the absence of this information, our scheme provides a default bidding policy.
+This ``backwards-compatible" mode must still perform comparable with DRF, especially given the current state of job requests.
+
+To investigate this feature, we ran our simulator using both DRF and the market-based mechanism under the default bidding policy.
+We ran under two cluster environments, a 25-node cluster to simulate high resource contention, and a 100-node cluster to simulate a light workload.
+All nodes were homogeneous, with normalized CPU, RAM, and disk resources of 1.
+We ran using a statistical workload for five computing frameworks, each submitting 20 jobs in parallel.
+For each environment, we evaluated the resource utilization and job completion times of DRF and the market-based mechanism.
+
+Figures CPU-UTILIZATION and RAM-UTILIZATION show the CPU and RAM utilizations of DRF and the market-based mechanism in the high contention environment.
+As noted, the Google traces indicated cluster jobs were primarily CPU-bound, and hence the cluster witnesses near-maximal CPU utilization but lower RAM utilization.
+Figure CPU-UTILIZATION indicates that the utilization achieved by DRF and the default bidding policy are nearly identical.
+The average DRF utilization is approximately 98\%, while the market-based mechanism is approximately 99\%.
+Note the graph begins after 10 hours, when consistent maximum contention is reached.
+Figure RAM-UTILIZATION depicts the memory utilization, showing again the similar performance between DRF and the market-based mechanism.
+DRF's average memory utilization is TODO\%, while the market-based mechanism's average memory utilization is TODO\%.
+We do not show the disk utilization because very few jobs in the Google traces used local disk space (presumably instead relying on the Google File System).
+
+Figure CPU-UTILIZATION-LOW shows the CPU utilizations of DRF and the market-based mechanism in a low contention environment, when no resource is fully utilized.
+As we can see, DRF and the market-based mechanism perform nearly identical.
+Both policies have an average CPU utilization of 44\%.
+We elide the memory and disk utilization figures because they repeat the same story, but are less interesting due to the lower RAM and disk resource requirements of jobs.
+
+Finally, Figure JOB-COMPLETION displays the progression of workload completion under both scheduling policies.
+When all tasks of a job are completed, the job is considered finished.
+The graph shows the fraction of complete jobs as time progresses.
+Again, both policies result in similar behaviour, completing the workload in nearly identical fashion.
+
+All of these results are gathered when the market-based mechanism uses a default bidding policy because the job requests provide no economic information.
+This shows that the market-based mechanism is ``backwards-compatible" by providing comparable performance to DRF when pricing information is not used.
+This result is not completely surprising though, because the default bidding policy behaves similarly to DRF.
+DRF awards resources to the framework with the least dominant share.
+Under our default bidding policy, frameworks bid a proportion of their current budget.
+The framework that has been awarded the least resources will have the highest budget (through less spending on resources), and will be able to bid the highest.
+Hence the low-resource framework will be awarded the next resource offer, similarly to DRF.
+
+\subsection{Performance With Pricing}
 
@@
 \label{sec:conclusion}
+
+\section{Acknowledgement}
+
+We thank Professors Anthony Joseph and John Kubiatowicz for guidance and numerous suggestions throughout the course of this project.
+Also, we thank Charles Reiss for providing helpful tips on how best to use the Google cluster traces.
+Finally, we thank Ali Ghodsi for providing meaningful discussion into the theory behind our market-based mechanism.
+
 %

### 2013-12-17 paper/paper.tex

@@
 
-\subsection{Performance With Pricing}
+\subsection{Performance With Pricing\\}
+
+When pricing information is provided, we show that the market-based mechanism can provide better performance than in DRF.
+As discussed in Section TODO, there are many situations in which prices can be used to better encapsulate a framework's preferences.
+As a case study, we investigate one particular scenario of inhomogeneous performing resources.
+
+In this case, we assume certain nodes have a special resource that significantly improves job performances, while the remaining nodes do not.
+In a realistic case, this special resource could be a GPU, which can significantly reduce CPU-bounded job completion times.
+While most jobs will see some performance benefits from running on a GPU, some jobs may be specifically crafted for optimal performance on a GPU, and hence will see the largest performance improvement if run on a GPU.
+
+The current Mesos implementation does not recognize this special sort of inhomogeneous performing resource.
+However, if a framework is aware of the inhomogeneous performing resource, it can schedule tasks appropriately on slaves when offered, such that the tasks that benefit most from special resources will be scheduled on special resource slaves.
+For the simulations, we have implemented the framework scheduler in such a manner.
+For the market-based mechanism, we use a bidding policy proportional to the default bidding policy.
+However, when a task can benefit from a special slave by a speedup factor $s$, the default bid is multiplied by $\frac{1}{s}$, resulting in a bid that is inversely proportional to the speedup factor.
+
+We simulate this scenario using a 64-node cluster, where 16 nodes have the special resource.
+Jobs from the statistical workload are uniformly randomly assigned one of two speedup factors, such that all tasks in a job experience the same speedup factor.
+The ``slow" speedup reduces task runtime by 10\%, while the ``fast" speedup reduces task runtime by 90\%.
+All tasks with a ``fast" speedup are marked as preferring a special resource slave, and a framework in DRF Mesos will schedule a ``fast" task on a special resource slave if possible.
+The workload was again generated for five frameworks, with up to 20 jobs running in parallel.
+
+Figure JOB-COMPLETION depicts the time progression of job completions, where a job is considered finished when all of its tasks are finished.
+As the figure depicts, the market-based mechanism is consistently ahead of DRF at all times, and finishes all jobs in about 20\% less time than DRF.
+Looking in detail, we find that DRF schedules only 30\% of ``fast" tasks on special resource slaves, while the market-based mechanism schedules 60\%.
+One might note that around the eighth hour, it appears DRF catches up to the market-based mechanism before falling behind again.
+This effect is caused by a long running job that the market-based mechanism schedules earlier than DRF.
+Its completion progresses the fraction of job completion minimally yet accounts for a long period of time.
+This allows DRF, which is still completing earlier short-lived tasks, to momentarily catch up in the fraction of job completion.
+When DRF schedules the same long-lived job at a latter point, it once again lags behind the market-based mechanism.
+
+Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences than DRF, resulting in better performance for the market-based mechanism.
+DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others.
+By better scheduling jobs on machines that best complete them, we see the overall performance improvements of the market-based mechanism.
 

### 2013-12-17 auction.cpp
Changes I don't remember plus a merge, sorry.

@@ -10,9 +10,9 @@
 
 #include <glog/logging.h>
 
+#include "mesos.hpp"
 #include "auction.hpp"
 #include "shared.hpp"
-#define RATE = 0.01
 
 using namespace std;
 
@@ -44,12 +44,14 @@ Auction::Auction(
     const unordered_map<FrameworkID, vector<vector<Bid> > >& _all_bids,
     const unordered_map<SlaveID, Resources>& _resources,
     const Resources& _reservation_price, const double _min_price_increase,
-    const double _price_multiplier)
+    const double _price_multiplier,
+    const Indexer<Slave>& _all_slaves)
     : all_bids(_all_bids),
       resources(_resources),
       reservation_price(_reservation_price),
       min_price_increase(_min_price_increase),
-      price_multiplier(_price_multiplier) {}
+      price_multiplier(_price_multiplier),
+      all_slaves(_all_slaves) {}
 
 bool Auction::displace(const Bid& new_bid, vector<Bid*>& displaced_bids,
                        double& total_cost) {
@@ -58,9 +60,9 @@ bool Auction::displace(const Bid& new_bid, vector<Bid*>& displaced_bids,
 
   // Compute how much more resources we need to accomodate the new bid.
   SlaveID slave_id = new_bid.slave_id;
-  if (!(new_bid.requested_resources < resources[slave_id])) {
+  if (!(new_bid.requested_resources < all_slaves[slave_id].free_resources)) {
     VLOG(2) << "    Slave too small: " << new_bid << " will never fit in "
-            << resources[slave_id];
+            << all_slaves[slave_id].free_resources;
     return false;
   }
 
@@ -105,10 +107,6 @@ bool Auction::displace(const Bid& new_bid, vector<Bid*>& displaced_bids,
       return true;
     }
   }
-
-  // Total resources were not enough despite the check above.
-  LOG(FATAL) << "    Failure: " << freed_resources << " < " <<
-    needed_resources;
 
   return false;
 }

### 2013-12-17 auction.hpp

@@ -5,6 +5,7 @@
 #include <vector>
 #include <string>
 
+#include "mesos.hpp"
 #include "shared.hpp"
 
 using namespace std;
@@ -28,7 +29,7 @@ class Auction {
   Auction(const unordered_map<FrameworkID, vector<vector<Bid>>>& _all_bids,
           const unordered_map<SlaveID, Resources>& _resources,
           const Resources& _reservation_price, const double _min_price_increase,
-          const double _price_multiplier);
+          const double _price_multiplier, const Indexer<Slave>& _all_slaves);
 
   void run();
 
@@ -46,6 +47,7 @@ class Auction {
   unordered_map<SlaveID, Resources> resources;
   Resources reservation_price;
 
+  const Indexer<Slave>& all_slaves;
   unordered_map<SlaveID, vector<Bid*>> winning_bids_per_slave;
 
   const double min_price_increase;

### 2013-12-17 mesos.hpp

@@ -57,10 +57,14 @@ struct Task : public Indexable {
   std::unordered_set<size_t> remaining_dependencies;
 };
 
+DECLARE_double(cpu);
+DECLARE_double(mem);
+DECLARE_double(disk);
+
 class Slave : public Indexable {
  public:
-  Slave() : resources({ 10, 10000, 1 }),
-            free_resources({ 10, 10000, 1 }) {}
+  Slave() : resources({ FLAGS_cpu, FLAGS_mem, FLAGS_disk }),
+            free_resources({ FLAGS_cpu, FLAGS_mem, FLAGS_disk }){};
   Resources resources;
   std::unordered_set<size_t> curr_tasks;
   Resources free_resources;

### 2013-12-17 mesosSim.cpp

@@ -22,6 +22,7 @@
 #include "simulation.hpp"
 #include "mesos.hpp"
 
+
 using namespace std;
 
 // i have decided to go for a priority queue based simulation; the caveat is
@@ -96,6 +97,8 @@ class MesosSimulation : public Simulation<MesosSimulation> {
 
   void update_budget(Framework& f, double time);
 
+  void log_utilization();
+
   unordered_map<size_t, Resources> all_free_resources() const;
   void offer_resources(size_t framework_id,
                        unordered_map<size_t, Resources> resources, double now);
@@ -119,6 +122,8 @@ class MesosSimulation : public Simulation<MesosSimulation> {
 
   bool ready_for_auction;
   bool currently_making_offers;
+
+  int gg = 0, bb = 0, bg = 0, gb = 0;
 };
 Resources MesosSimulation::total_resources;
 Resources MesosSimulation::used_resources;
@@ -131,6 +136,9 @@ DEFINE_string(policy, "drf",
 DEFINE_string(trace, "synthetic_workload.txt",
     "Path to trace for trace_workload.");
 DEFINE_string(validation, "validation.log", "Filename of validation logs");
+DEFINE_double(cpu, 0.5, "CPU per slave");
+DEFINE_double(mem, 0.5, "Memory per slave");
+DEFINE_double(disk, 0.5, "Disk per slave");
 
 void rand_workload(int num_frameworks, int num_jobs, int num_tasks_per_job,
                    Indexer<Framework>& allFrameworks, Indexer<Task>& allTasks,
@@ -380,6 +388,21 @@ void MesosSimulation::start_task(
 
     f.task_started(task.id(), now);
 
+    if (slave.special_resource){
+        if (task.special_resource_speedup  < 0.5){
+            gg++;
+        } else{
+            gb++;
+        }
+    } else{
+        if (task.special_resource_speedup < 0.5){
+            bg++;
+        } else{
+            bb++;
+        }
+    }
+
+
     if (DEBUG) {
       cout << "Slave scheduled: id=" << slave.id()
            << " cpu: " << slave.free_resources.cpus
@@ -458,10 +481,7 @@ void OfferEvent::run(MesosSimulation& sim) {
 
   //cout << "Offers made at time " << << endl;
   //Log utilization
-  cout << sim.get_clock() / 1000000 << " " << sim.used_resources.cpus << " "
[…]

### 2013-12-17 plot.py

@@ -15,11 +15,9 @@ ax.xaxis.grid(b=True, which='both')
 plt.xlabel("time (in hours)")
 plt.ylabel("CPU utilization")
 plt.title("CPU utilization")
-plt.axis([0,90000/3600,0,1])
-plt.plot(drf[:,0]/3600.0, drf[:,1]/drf[:,2], label="DRF")
-plt.plot(auction[:,0]/3600.0, auction[:,1]/auction[:,2], label="Auction")
-plt.plot(roundrobin[:,0]/3600.0, roundrobin[:,1]/roundrobin[:,2], label="Round Robin")
-
+#plt.axis([0,180000/3600,0,1])
+plt.step(drf[:,0]/3600.0, drf[:,1]/drf[:,2], label="DRF")
+plt.step(auction[:,0]/3600.0, auction[:,1]/auction[:,2], label="Auction")
 plt.legend(loc="center right") 
 plt.show()
 
@@ -28,12 +26,11 @@ ax.yaxis.grid(b=True, which='both')
 ax.set_xticks(range(50))
 ax.xaxis.grid(b=True, which='both')
 
-plt.xlabel("time (in hours)")
-plt.ylabel("Memory utilization")
-plt.title("Memory utilization")
-plt.axis([0,90000/3600,0,1])
-plt.plot(drf[:,0]/3600.0, drf[:,3]/drf[:,4], label="DRF")
-plt.plot(auction[:,0]/3600.0, auction[:,3]/auction[:,4], label="Auction")
-plt.plot(roundrobin[:,0]/3600.0, roundrobin[:,3]/roundrobin[:,4], label="Round Robin")
-plt.legend(loc="center right") 
-plt.show()
+#plt.xlabel("time (in hours)")
+#plt.ylabel("Memory utilization")
+#plt.title("Memory utilization")
+#plt.axis([0,180000/3600,0,1])
+#plt.plot(drf[:,0]/3600.0, drf[:,3]/drf[:,4], label="DRF")
+#plt.plot(auction[:,0]/3600.0, auction[:,3]/auction[:,4], label="Auction")
+#plt.legend(loc="center right") 
+#plt.show()

### 2013-12-17 statistical_workload.py

@@ -1,6 +1,6 @@
 from collections import defaultdict
 import argparse
-import pickle
+import cPickle as pickle
 from random import *
 import sys
 
@@ -66,7 +66,7 @@ def generate_tasks(statistics, frameworks, n, acceleration=False):
     if type(frameworks) == int:
         frameworks = range(frameworks)
     while len(result) < n:
-        framework = choice(frameworks)
+        framework = choice(frameworks[:len(frameworks)/2] + 4*frameworks[len(frameworks)/2:])
         tasks = sample_tasks(jobs, counts, acceleration)
         for task in tasks:
             task['task_id'] = task_id
@@ -89,6 +89,13 @@ def print_tasks(tasks, filename="synthetic_workload.txt", num_users =1):
             if t['framework'] in current_job and current_job[t['framework']] != t['job_id']:
                 last_job[t['framework']] = [current_job[t['framework']]]
             current_job[t['framework']] = t['job_id']
+            if t['framework'] / num_users == 0:
+                t['acceleration'] = 0.9
+            elif t['framework'] / num_users == 1:
+                t['acceleration'] = 0.1
+            else:
+                print('framework is: {}'.format(t['framework']))
+            print('acceleration is: {}'.format(t['acceleration']))
             serialized = [ t['job_id'], counts[t['job_id']], 0, t['time'], t['framework'] / num_users, 0, 0, t['cpu'], t['ram'], t['disk'], t['acceleration']] + last_job[t['framework']]
             counts[t['job_id']] += 1
             f.write(' '.join(str(x) for x in serialized) + '\n')

### 2013-12-17 image_1/plot.py
Added scratchwork for generating diagrams

@@ -1,0 +1,35 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import sys
+
+print(sys.argv)
+drf = np.loadtxt(sys.argv[1])
+auction = np.loadtxt(sys.argv[2])
+plt.xlabel("time (in hours)")
+plt.ylabel("CPU utilization")
+plt.title("Utilization of auctions vs. DRF (heavy workload)")
+#plt.axis([0,180000/3600,0,1])
+plt.rc('font', size=18)
+print(drf[:,0])
+print(auction)
+
+plt.step(drf[:,0]/3600.0, drf[:,1], label="DRF")
+plt.step(auction[:,0]/3600.0, auction[:,1], label="Auction")
+leg = plt.legend(loc="lower right") 
+for legobj in leg.legendHandles:
+        legobj.set_linewidth(2.0)
+plt.show()
+
+#fig,ax = plt.subplots()
+#ax.yaxis.grid(b=True, which='both')
+#ax.set_xticks(range(50))
+#ax.xaxis.grid(b=True, which='both')
+
+#plt.xlabel("time (in hours)")
+#plt.ylabel("Memory utilization")
+#plt.title("Memory utilization")
+#plt.axis([0,180000/3600,0,1])
+#plt.plot(drf[:,0]/3600.0, drf[:,3]/drf[:,4], label="DRF")
+#plt.plot(auction[:,0]/3600.0, auction[:,3]/auction[:,4], label="Auction")
+#plt.legend(loc="center right") 
+#plt.show()

### 2013-12-17 image_1/summarize.py

@@ -1,0 +1,22 @@
+import sys
+
+LOWER = 50000
+UPPER = 182000
+STEP = 100
+
+with open(sys.argv[1], 'r') as f:
+    pts = [(float(x.split(" ")[0]), float(x.split(" ")[1]) / float(x.split(" ")[2])) for x in f]
+
+index = 0
+smoothed = []
+for i in range(LOWER, UPPER, STEP):
+    in_range = [pts[index]]
+    while index < len(pts) and pts[index][0] < i + STEP:
+        index+=1
+        if index < len(pts):
+            in_range.append(pts[index])
+    smoothed.append((sum(x[0] for x in in_range)/len(in_range), sum(x[1] for x in in_range)/len(in_range)))
+
+with open(sys.argv[2], 'w') as f:
+    for x in smoothed:
+        f.write("{} {}\n".format(x[0], x[1]))

### 2013-12-17 image_2/average.py

@@ -1,0 +1,14 @@
+import sys
+
+a = []
+
+with open(sys.argv[1], 'r') as f:
+    for x in f:
+        xs = x.split(" ")
+        a.append([int(xs[0]), float(xs[1]) / float(xs[2])])
+
+s = 0
+for i in range(1, len(a)):
+    s += (a[i][0] - a[i-1][0]) * a[i][1]
+
+print(s / (a[-1][0]  - a[0][0]))

### 2013-12-17 image_2/plot.py

@@ -1,0 +1,35 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import sys
+
+print(sys.argv)
+drf = np.loadtxt(sys.argv[1])
+auction = np.loadtxt(sys.argv[2])
+plt.xlabel("time (in hours)")
+plt.ylabel("CPU utilization")
+plt.title("Utilization of auctions vs. DRF (light workload)")
+#plt.axis([0,180000/3600,0,1])
+plt.rc('font', size=18)
+print(drf[:,0])
+print(auction)
+
+plt.step(drf[:,0]/3600.0, drf[:,1], label="DRF")
+plt.step(auction[:,0]/3600.0, auction[:,1], label="Auction")
+leg = plt.legend(loc="lower right") 
+for legobj in leg.legendHandles:
+        legobj.set_linewidth(2.0)
+plt.show()
+
+#fig,ax = plt.subplots()
+#ax.yaxis.grid(b=True, which='both')
+#ax.set_xticks(range(50))
+#ax.xaxis.grid(b=True, which='both')
+
+#plt.xlabel("time (in hours)")
+#plt.ylabel("Memory utilization")
+#plt.title("Memory utilization")
+#plt.axis([0,180000/3600,0,1])
+#plt.plot(drf[:,0]/3600.0, drf[:,3]/drf[:,4], label="DRF")
+#plt.plot(auction[:,0]/3600.0, auction[:,3]/auction[:,4], label="Auction")
+#plt.legend(loc="center right") 
+#plt.show()

### 2013-12-17 paper/paper.tex
Added theory section (draft -1)

@@
 
+\section{Theoretical analysis}
+
+\subsection{Drawbacks of non-economic scheduling}
+Most scheduling policies used in practice do not use any economic information: clients request resources, and schedulers allocate those resources.
+Clients may be assigned priorities and/or budgets which are used by the scheduler to determine how many resources to assign to that client, but requests themselves are an all-or-nothing affair.
+
+These policies can work well when the scheduler is aware of all of the relevant constraints faced by clients.
+But when constraints are invisible to the scheduler, as is the case in Mesos, this paradigm can become problematic.
+Approaches like lottery scheduling (though not in fact used in Mesos) can partly get around these problems by ensuring that each client receives a proportional share of every resource type, even if the differences between resources are not known to the scheduler.
+But these techniques cannot easily ensure that a resource is given to the framework that needs it most.
+
+In this section we prove some theorems that make this difficulty more concrete.
+Our results illustrate the general theme that the theoretical guarantees of fairness-based schedulers are highly brittle to realistic variations in the model.
+All of our results are straightforward consequences of well-understood limitations in mechanism design.
+We feel that these limitations are real and applicable to scheduling problems, and that they show fairly clearly that strong theoretical guarantees like strategy-proofness are not pragmatically desirable.
+This is in concordance with the dominance of mechanisms which are not strategy-proof in most complex environments.
+We stress that the results in this section are primarily intended to illustrate the limited applicability of the theoretical analysis of existing schedulers (and hence to excuse the lack of such analysis for our own system) rather than to directly demonstrate practical superiority.
+
+We will use the suggestive term “realistic conditions” to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
+
+Users have time-varying demands and tasks of varying importance.
+Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
+Users face deadlines.
+Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources.
+Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.
+
+We say that a system is “demand-based” if it elicits a demand from each user and makes assignments on the basis of the stated demands.
+For example, DRF, asset allocation, and CEEI all fall into this class.
+
+Theorem 1. Any demand-based system which is Pareto efficient under realistic conditions must sometimes assign the entire cluster to a single user, an extreme violation of fairness.
+
+Proof: We provide the proof for the time-varying demands case.
+The other arguments are exactly analogous.
+We give an extremely simple and artificial case, though analogous behavior would be expected in more realistic cases.
+
+Suppose that there are two users and that at each time each user has enough tasks to consume all of the clusters’ resources.
+Tasks arrive at multiples of time T and last for T rounds.
+Moreover, suppose that during each interval of time T each user has an independently and uniformly randomly generated priority which is either “high” or “low.” The only characteristic of these priorities is that, all else equal, they would prefer run one extra high priority task at the expense of one fewer low priority task.
+
+Since the scheduler is demand-based and the user’s priority levels are changing across time, the allocation must be independent of the priority of the users.
+So if each user receives a non-zero share of the resources, then each user must receive a non-zero share of the resources while they are in the “high” priority state and the other user is in the “low” priority state.
+
+But now consider the alternative allocation which exchanges these periods, i.e.
+assigns each user R resources more during their high priority period and R resources fewer during their low priority period.
+By definition, this alternative allocation is preferred to the real allocation, contradicting Pareto efficiency.
+
+Theorem 2.
+Under realistic conditions, the implementation of DRF in Mesos is not strategy-proof, Pareto efficient, envy-free, or compatible with the sharing incentive.
+DRF satisfies a weaker form of strategy-proofness, “look-ahead strategy proofness,” such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler’s future behavior.
+
+Proof: For variety, we consider the case of inhomogeneous resources.
+Again, the proof is identical in any of the given cases.
+For each property we construct a special situation in which DRF fails to achieve that property.
+
+Strategy-proofness: consider the setting where a framework’s top priority is achieving some particularly valuable resource X which is currently in use, though they have other tasks which they value less.
+To be most extreme, suppose the user values any outcome in which they receive X higher than any outcome in which they do not.
+A user can arrange to receive X by strategically passing up resource offers which they could use, in order to maximize their probability of being offered the resource X when it first becomes free.
+DRF is only “strategy-proof” in the sense that a user who anticipates all future behavior of the scheduler will honestly state whether they want a resource in light of the consequences on the scheduler.
+Pareto-efficiency: This is a corollary of the preceding theorem.
+In the case of inhomogeneous resources, suppose that two users have streams of tasks, some of which run faster on resources of type A and some of which run faster on resources of type B.
+Then no demand-based scheduler can ensure that tasks are always placed on the resources on which they run fastest.
+Envy-freeness and compatibility with sharing incentive: Suppose that one user consumes ⅓ of the resources in the cluster and another consumes ½ of the resources, but a particular 10% of the resources in the cluster are several times more valuable (to every user) than they appear.
+This could be based on hardware characteristics to which the scheduler is oblivious.
+The user who consumes ⅓ of the resources receives all resource offers first, and so claims all 10% of these resources.
+But this means that this user receives significantly more total value than the other user, violating both envy-freeness and the sharing incentive.
+
+Theorem 3. The sharing incentive and Pareto efficiency are incompatible for demand-based systems which deal with time-varying demands of varying importance.
+
+Proof: %XXX, Insert proof, it’s super straightforward]
+\subsection{Virtues of economic scheduling}
+In this section, we show that our system possesses weaker versions of the theoretical guarantees of the theoretical properties that have been ascribed to existing schedulers.
+In light of the arguments in the preceding section, we hope to illustrate that the two systems are on comparable theoretical footings.
+
+The first theorem considers the setting in which user’s willingness to pay [XXX continue]
+
+Theorem 4.
+[Sharing incentive] Each user A values the total resources they receive at least as much as they value their share of the cluster (i.e.
+the amount paid by A divided by the entire cost paid by all users of the cluster).
+
+Proof: Consider a particular user A. During any auction, let $p_A$ be the price that $A$ pays, 
+let $p_B$ be the price paid by all other users, let $R_A$ be the resources received by A, and let $R_B$ be the resources received by all other users.
+The key point is that user A values $R_A$ at at least $p_A$, and values $R_B$ at at most $p_B$.
+Thus user A values their share of the resources at at least $\frac {p_A}{p_A + p_B}$.
+
+%XXX finish proof, very easy.
+
+Theorem 5.
+Using a closed currency, if the rate of income of a particular user is p, that user can adopt a bidding strategy which ensures that they receive a p fraction of the cluster during any period of length T, where T is an upper bound for the length of a task (i.e.
+the maximum of the minimum amount of time after which any task can be revoked).
+
+Proof:
+
 \section{Market-based Mechanism Design}

### 2013-12-17 paper/paper.tex
Add most of related work section

@@
 % 3rd. author
-\email{\{paulchristiano, frankli, ricshin\}@cs.berkeley.edu}
+\email{\{paulfchristiano, frankli, ricshin\}@cs.berkeley.edu}
 %\and  % use '\and' if you need 'another row' of author names
@@
 
-\section{Future Works}
+\section{Related Work}
+\subsection{Grid computing}
+Job schedulers like TORQUE \cite{torque}, Condor \cite{condor}, and LSF
+\cite{lsf} have long been used for solving the problem of resource allocation
+within a high-performance-computing (HPC) or grid-computing environment.
+For the most part, they do not use a two-level scheduling model like we do but
+instead operate as a queue for predefined jobs which are run as resources become
+available. Machines and job requirements also tend to show more homogeniety
+within such environments (for example, the ratio between CPU, memory, and disk),
+so sthe amount of optimization possible with pricing is lower.
+
+\subsection{Cloud and datacenter computing}
+Our work depends heavily on Mesos~\cite{mesos}, as we use its model of
+resources, tasks, and frameworks as the basis for our own. We also use Mesos as
+a baseline for purposes of comparison, as we have already extensively discussed.
+
+Jockey~\cite{jockey} attempts to solve the specific problem of adjusting
+resource allocation in the datacenter environment to ensure important jobs
+finish within deadlines. They do not directly modify the scheduler for this but
+instead adjust the priority of each job as needed within an existing system.
+With our work, we attempt to create a general-purpose system which can solve not
+only the problem of deadlines, but also allow expression of many different kinds
+of demands and have them all interact nicely with each other without needing
+specialized logic to keep track of each one explicitly.
+
+\subsection{Resource allocation}
+Dominant resource fairness~\cite{drf}
+
+\subsection{Economics/pricing in computer systems}
+Lottery scheduling
+
+\subsection{Economics/pricing for resource allocation}
+Many previous researchers have proposed systems which use ideas from economics
+to assign resources in computer systems.  Analogous to our datacenter
+implementation, \cite{stoica94} uses prices, budgets, and auctions for
+scheduling within a single machine. It ensures some level of fairness and
+allows low-income but mostly-idle users to occasionally spend more money beyond
+their income for urgent jobs by drawing upon their account balance. However,
+resource demands are much more homogeneous in this environment than within a
+datacenter, so the usefulness of prices as a vehicle for expressing prices are
+more limited. Spawn \cite{spawn} uses auctions to rent time-slices of idle
+workstations; rather than using prices as a priority-indicating mechanism
+automatically set based on application requirements, this work places more
+emphasis on using it for reimbursement where users manually allocate budgets to
+jobs. Tycoon \cite{tycoon} also uses auctions to divide up the cluster's
+resources among competing users, except the auctions are used for CPU scheduling
+within each individual machine rather than for setting bounds on allowed
+resource usage of each job, and has no provision for the presence of
+multiple contentious resources.
+
+More generally, fair division is the problem in economics of dividing a set of
+resources equitably among a set of people. Our problem differs somewhat from
+fair division in that we don't seek to allocate every bit of the cluster to the
+set of users. We assume that a user might be happy to have received nothing if
+their value of gaining resources was too low compared to the others, since the
+user keeps some amont of money unspent as a a result.
+
+One of the economic fair division solutions is CEEI~\cite{moulin2004fair}, or
+competitive equilibrium from equal incomes. This mechanism emulates a market
+where participants initially receive an equal amount of resources and trade some
+of them until each has the desired amount of resources. CEEI's use of a market
+differs significantly from ours in that we do not use it only as a vehicle for
+achieving a fair allocation, but also for frameworks to express their
+preferences in a fine-grianed way using prices and willingness to pay.
+
+\section{Discussion and Future Work}
 \label{sec:future}
@@
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file

### 2013-12-17 paper/paper.tex
Write more about auction

@@
 \documentclass{acm_proc_article-sp}
+
+\usepackage{mathtools}
+\usepackage{graphicx}
 
@@
 \label{sec:design}
+\subsection{Setting}
+Our mechanism assumes three types of participants: a single \emph{master} for
+the cluster which manages a large number of \emph{slaves} serving as a pool of
+compute resources. The users of the system are represented by \emph{frameworks},
+which communicate with the master to request resources on slaves, and use the
+obtained resources to run \emph{tasks} on the slaves.
+
+These participants generally run as daemons on the cluster.  Typically, a single
+cluster would consist of up to tens of thousands of machines, each of which
+running a slave process. A single master process (or multiple redundant ones
+for reliability) communicates directly with all slave processes.  Each slave
+process manages the tasks which run on its machine, handling requests to start
+and stop various tasks from the master.
+
+The frameworks representing the clusters also run as daemons and register
+themselves with the master. They communicate exclusively with the master, which
+mediates all needed communication with the slaves, such as details on the task
+to be run.
+
+\subsection{Budgets and income}
+The master keeps track of a budget for each framework: its current balance and
+the amount of income it receives per second. The automatically adjusts a
+framework's balance when it performs actions which require payment. Currently,
+we allow a framework to incur a negative income (if it is spending beyond its
+means) and also a negative balance (if negative income lasts long enough to
+remove all of the savings) for simplicity.
+
+\subsection{Resource offers and bidding}
+Periodically, when there are resources currently available, the master will
+send a \emph{resource offer} message to all registered frameworks to invite them
+to participate in an upcoming auction. Each framework then submits a package of
+bids, which we can consider a function of the form
+\[ \mathcal{B}: \mathbf{T}^n \rightarrow \mathbf{R}. \]
+where there are $n$ slaves, $T$ is a task (containing an amount of desired
+resources on a single slave) and $\mathbf{R}$ is a willingness to pay for the
+list of tasks $\mathbf{T}^n$.
+
+A naive representation of this function would use an exponential amount of
+space, given that each of the $n$ values in $\mathbf{T}^n$ can vary
+independently. While we can consider several methods for restricting the set of
+possible
 

### 2013-12-17 paper/paper.tex
Write a little bit more

@@
 \[ \mathcal{B}: \mathbf{T}^n \rightarrow \mathbf{R}. \]
-where there are $n$ slaves, $T$ is a task (containing an amount of desired
-resources on a single slave) and $\mathbf{R}$ is a willingness to pay for the
+where there are $n$ slaves, $\mathbf{T}$ is a task (containing an amount of desired
+resources on a single slave) and $\mathbf{R}$ is the willingness to pay for the
 list of tasks $\mathbf{T}^n$.
@@
 space, given that each of the $n$ values in $\mathbf{T}^n$ can vary
-independently. While we can consider several methods for restricting the set of
-possible
+independently. While we can consider several methods greatly varying in
+complexity for encoding this function more compactly, we use the following
+two-level representation:
+\begin{itemize}
+  \item A list of \emph{task packages}, with the assumption that the willingness
+    to pay for any subset of the list is simply the sum of the willingness to
+    pay for each element in the subset
+  \item A list of tasks in each task package, with a specific slave and a
+    willingness to pay for each task. The auction assumes that the framework
+    desires only one of the tasks and values all of them equally.
+\end{itemize}
+While this obviously cannot represent all possible $\mathcal{B}$, it still
+allows enough flexibility to, e.g., pay more to have a task run on a faster
+machine than a slower one.
+
+\subsection{Ascending-bid clock auction}
+Once the master has collected a set of bids, it uses an ascending-bid clock
+auction to determine which of the bids to fulfill, and how much it should charge
+for each of the tasks which win the auction. The auction consists of a number of
+rounds which continue until no changes occur in the final round. To avoid the
+need for communication between the master and the frameworks after each round,
+we use a \emph{proxy auction} where each framework makes a single bid for all
+rounds and agents running with the master represent each of them within the
+master.
+
+Specifically, the auction tries to fit bids into the available resources in the
+cluster as to maximize the amount of revenue from the auction. With each task
+package, we associate a \emph{current price} in addition to the willingness to
+pay; then the difference between the latter and the former is  the The agent
+representing a framework's bid computes
 

### 2013-12-17 paper/paper.tex
Write a little bit more

@@
 
-Specifically, the auction tries to fit bids into the available resources in the
-cluster as to maximize the amount of revenue from the auction. With each task
-package, we associate a \emph{current price} in addition to the willingness to
-pay; then the difference between the latter and the former is  the The agent
-representing a framework's bid computes
+With each set of tasks, we associate a \emph{current price} in addition to the
+willingness to pay; then the difference between the latter and the former is the
+profit incurred by the framework for that set of tasks. The agent representing a
+framework's bid initially sets the current price to equal a \emph{reserve price}
+based on the amount of resources within the bid.
+
+For the master, the goal of the auction is to pick a set of tasks to run which
+is feasible (i.e., does not use resource beyond what is currently available) and
+which maximizes the revenue (the sum of the \emph{current price} for each of the
+tasks).
+
+The auction operates by maintaining a set of winners, and asking each of
+the frameworks' agents in turn to suggest a change to the set such that it
+remains feasible and increases the master's revenue. The agent then takes an
+action to maximize its represented framework's profit by putting as many tasks
+as possible into the winning set. If the agent needs to evict some current
+winners to make room for tasks that it wants to run, then it must raise the
+current price of the tasks by an amount which exceeds the current price of the
+evicted tasks; sometimes that may cause the current price to exceed the task's
+willingness to pay, which indicates that there is too much competition driving
+up the price to profitably run the task on the cluster at this time.
+
+\subsection{Bidding policy}
+Given a set of tasks it wishes to run, the framework must
 

### 2013-12-17 paper/paper.tex
Write a little bit more

@@
 \subsection{Bidding policy}
-Given a set of tasks it wishes to run, the framework must
+Within our setting, the framework must associate a willingness to pay with each
+task it wishes to run. We now describe some reasonable ways for the frameworks
+to do so.
+
+\paragraph{Default policy} For backwards compatibility, we want to be able to
+use existing Mesos frameworks which are not aware of prices. For these, we
+define a default bidding policy which assumes that all tasks are equally
+important.
+
+Intuitively, a framework with higher income can afford to have a higher
+willingness to pay. A framework which has accumulated a lot of money can also
+afford to pay more, at least for a limited amount of time before its balance is
+exhausted. Also, tasks which require more resources should have a
+correspondingly higher willingness to pay.
 

### 2013-12-18 paper/paper.tex
Added property table, added eval graphs

@@
 \usepackage{graphicx}
+\usepackage{amssymb}
+\usepackage{pifont}
+\newcommand{\cmark}{\ding{51}}%
 
@@
 protocol remains backwards-compatible, and can be applied without any change to
-the clients’ code.
+the clients' code.
 
@@
 This example clearly shows that in this case, the mechanism provided by Mesos is
-\emph{not} strategy-proof. Worse, it’s not Pareto efficient if people are
+\emph{not} strategy-proof. Worse, it's not Pareto efficient if people are
 honest, and need not be Pareto efficient if clients behave optimally. Similar
@@
 
-\section{Theoretical analysis}
-
-\subsection{Drawbacks of non-economic scheduling}
-Most scheduling policies used in practice do not use any economic information: clients request resources, and schedulers allocate those resources.
-Clients may be assigned priorities and/or budgets which are used by the scheduler to determine how many resources to assign to that client, but requests themselves are an all-or-nothing affair.
-
-These policies can work well when the scheduler is aware of all of the relevant constraints faced by clients.
-But when constraints are invisible to the scheduler, as is the case in Mesos, this paradigm can become problematic.
-Approaches like lottery scheduling (though not in fact used in Mesos) can partly get around these problems by ensuring that each client receives a proportional share of every resource type, even if the differences between resources are not known to the scheduler.
-But these techniques cannot easily ensure that a resource is given to the framework that needs it most.
-
-In this section we prove some theorems that make this difficulty more concrete.
-Our results illustrate the general theme that the theoretical guarantees of fairness-based schedulers are highly brittle to realistic variations in the model.
-All of our results are straightforward consequences of well-understood limitations in mechanism design.
-We feel that these limitations are real and applicable to scheduling problems, and that they show fairly clearly that strong theoretical guarantees like strategy-proofness are not pragmatically desirable.
-This is in concordance with the dominance of mechanisms which are not strategy-proof in most complex environments.
-We stress that the results in this section are primarily intended to illustrate the limited applicability of the theoretical analysis of existing schedulers (and hence to excuse the lack of such analysis for our own system) rather than to directly demonstrate practical superiority.
-
-We will use the suggestive term “realistic conditions” to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
-
-Users have time-varying demands and tasks of varying importance.
-Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
-Users face deadlines.
-Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources.
-Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.
-
-We say that a system is “demand-based” if it elicits a demand from each user and makes assignments on the basis of the stated demands.
-For example, DRF, asset allocation, and CEEI all fall into this class.
-
-Theorem 1. Any demand-based system which is Pareto efficient under realistic conditions must sometimes assign the entire cluster to a single user, an extreme violation of fairness.
-
-Proof: We provide the proof for the time-varying demands case.
-The other arguments are exactly analogous.
-We give an extremely simple and artificial case, though analogous behavior would be expected in more realistic cases.
-
-Suppose that there are two users and that at each time each user has enough tasks to consume all of the clusters’ resources.
-Tasks arrive at multiples of time T and last for T rounds.
-Moreover, suppose that during each interval of time T each user has an independently and uniformly randomly generated priority which is either “high” or “low.” The only characteristic of these priorities is that, all else equal, they would prefer run one extra high priority task at the expense of one fewer low priority task.
-
-Since the scheduler is demand-based and the user’s priority levels are changing across time, the allocation must be independent of the priority of the users.
-So if each user receives a non-zero share of the resources, then each user must receive a non-zero share of the resources while they are in the “high” priority state and the other user is in the “low” priority state.
-
-But now consider the alternative allocation which exchanges these periods, i.e.
-assigns each user R resources more during their high priority period and R resources fewer during their low priority period.
-By definition, this alternative allocation is preferred to the real allocation, contradicting Pareto efficiency.
-
-Theorem 2.
-Under realistic conditions, the implementation of DRF in Mesos is not strategy-proof, Pareto efficient, envy-free, or compatible with the sharing incentive.
-DRF satisfies a weaker form of strategy-proofness, “look-ahead strategy proofness,” such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler’s future behavior.
-
-Proof: For variety, we consider the case of inhomogeneous resources.
-Again, the proof is identical in any of the given cases.
-For each property we construct a special situation in which DRF fails to achieve that property.
-
-Strategy-proofness: consider the setting where a framework’s top priority is achieving some particularly valuable resource X which is currently in use, though they have other tasks which they value less.
-To be most extreme, suppose the user values any outcome in which they receive X higher than any outcome in which they do not.
-A user can arrange to receive X by strategically passing up resource offers which they could use, in order to maximize their probability of being offered the resource X when it first becomes free.
-DRF is only “strategy-proof” in the sense that a user who anticipates all future behavior of the scheduler will honestly state whether they want a resource in light of the consequences on the scheduler.
-Pareto-efficiency: This is a corollary of the preceding theorem.
-In the case of inhomogeneous resources, suppose that two users have streams of tasks, some of which run faster on resources of type A and some of which run faster on resources of type B.
-Then no demand-based scheduler can ensure that tasks are always placed on the resources on which they run fastest.
-Envy-freeness and compatibility with sharing incentive: Suppose that one user consumes ⅓ of the resources in the cluster and another consumes ½ of the resources, but a particular 10% of the resources in the cluster are several times more valuable (to every user) than they appear.
-This could be based on hardware characteristics to which the scheduler is oblivious.
-The user who consumes ⅓ of the resources receives all resource offers first, and so claims all 10% of these resources.
-But this means that this user receives significantly more total value than the other user, violating both envy-freeness and the sharing incentive.
-
-Theorem 3. The sharing incentive and Pareto efficiency are incompatible for demand-based systems which deal with time-varying demands of varying importance.
-
-Proof: %XXX, Insert proof, it’s super straightforward]
-\subsection{Virtues of economic scheduling}
-In this section, we show that our system possesses weaker versions of the theoretical guarantees of the theoretical properties that have been ascribed to existing schedulers.
-In light of the arguments in the preceding section, we hope to illustrate that the two systems are on comparable theoretical footings.
-
-The first theorem considers the setting in which user’s willingness to pay [XXX continue]
-
-Theorem 4.
-[Sharing incentive] Each user A values the total resources they receive at least as much as they value their share of the cluster (i.e.
-the amount paid by A divided by the entire cost paid by all users of the cluster).
-
-Proof: Consider a particular user A. During any auction, let $p_A$ be the price that $A$ pays, 
-let $p_B$ be the price paid by all other users, let $R_A$ be the resources received by A, and let $R_B$ be the resources received by all other users.
-The key point is that user A values $R_A$ at at least $p_A$, and values $R_B$ at at most $p_B$.
-Thus user A values their share of the resources at at least $\frac {p_A}{p_A + p_B}$.
-
-%XXX finish proof, very easy.
-
-Theorem 5.
-Using a closed currency, if the rate of income of a particular user is p, that user can adopt a bidding strategy which ensures that they receive a p fraction of the cluster during any period of length T, where T is an upper bound for the length of a task (i.e.
-the maximum of the minimum amount of time after which any task can be revoked).
-
-Proof:
-
 \section{Market-based Mechanism Design}
@@
 cluster would consist of up to tens of thousands of machines, each of which
-running a slave process. A single master process (or multiple redundant ones
+runs a slave process. A single master process (or multiple redundant ones
 for reliability) communicates directly with all slave processes.  Each slave
 process manages the tasks which run on its machine, handling requests to start
-and stop various tasks from the master.
+and stop tasks from the master.
 
@@
 The master keeps track of a budget for each framework: its current balance and
-the amount of income it receives per second. The automatically adjusts a
-framework's balance when it performs actions which require payment. Currently,
-we allow a framework to incur a negative income (if it is spending beyond its
-means) and also a negative balance (if negative income lasts long enough to
-remove all of the savings) for simplicity.
+the amount of income it receives per second. It automatically adjusts a
+framework's balance when it performs actions which require payment. For simplicity,
+we allow a framework to incur a negative income and also a small temporary negative balance, although we do not accept bids from a framework with a negative balance.
 
@@
 For the master, the goal of the auction is to pick a set of tasks to run which
-is feasible (i.e., does not use resource beyond what is currently available) and
-which maximizes the revenue (the sum of the \emph{current price} for each of the
+is feasible (i.e., does not use resources beyond what is currently available) and
+which maximizes the revenue (the sum of the \emph{current prices} for each of the
 tasks).
@@
 
+\section{Theoretical analysis}
+
+\subsection{Drawbacks of non-economic scheduling}
+Most scheduling policies used in practice do not use any economic information: clients request resources, and schedulers allocate those resources.
+Clients may be assigned priorities and/or budgets which are used by the scheduler to determine how many resources to assign to that client, but requests themselves are an all-or-nothing affair.
+
+These policies can work well when the scheduler is aware of all of the relevant constraints faced by clients.
+But when constraints are invisible to the scheduler, as is the case in Mesos, this paradigm can become problematic.
+Approaches like lottery scheduling (though not in fact used in Mesos) can partly get around these problems by ensuring that each client receives a proportional share of every resource type, even if the differences between resources are not known to the scheduler.
+But these techniques cannot easily ensure that a resource is given to the framework that needs it most.
+
+In this section we prove some theorems that make this difficulty more concrete.
+Our results illustrate the general theme that the theoretical guarantees of fairness-based schedulers are highly brittle to realistic variations in the model.
+All of our results are straightforward consequences of well-understood limitations in mechanism design.
+We feel that these limitations are real and applicable to scheduling problems, and that they show fairly clearly that strong theoretical guarantees like strategy-proofness are not pragmatically desirable.
+This is in concordance with the dominance of mechanisms which are not strategy-proof in most complex environments.
+We stress that the results in this section are primarily intended to illustrate the limited applicability of the theoretical analysis of existing schedulers (and hence to excuse the lack of such analysis for our own system) rather than to directly demonstrate practical superiority.
+
+We will use the suggestive term ``realistic conditions" to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
+
+Users have time-varying demands and tasks of varying importance.
+Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
+Users face deadlines.
+Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources.
+Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.
+
+We say that a system is ``demand-based" if it elicits a demand from each user and makes assignments on the basis of the stated demands.
+For example, DRF, asset allocation, and CEEI all fall into this class.
+
+Theorem 1. Any demand-based system which is Pareto efficient under realistic conditions must sometimes assign the entire cluster to a single user, an extreme violation of fairness.
+
+Proof: We provide the proof for the time-varying demands case.
+The other arguments are exactly analogous.
+We give an extremely simple and artificial case, though analogous behavior would be expected in more realistic cases.
+
+Suppose that there are two users and that at each time each user has enough tasks to consume all of the clusters' resources.
+Tasks arrive at multiples of time T and last for T rounds.
+Moreover, suppose that during each interval of time T each user has an independently and uniformly randomly generated priority which is either ``high" or ``low." The only characteristic of these priorities is that, all else equal, they would prefer run one extra high priority task at the expense of one fewer low priority task.
+
+Since the scheduler is demand-based and the user's priority levels are changing across time, the allocation must be independent of the priority of the users.
+So if each user receives a non-zero share of the resources, then each user must receive a non-zero share of the resources while they are in the ``high" priority state and the other user is in the ``low" priority state.
+
+But now consider the alternative allocation which exchanges these periods, i.e.
+assigns each user R resources more during their high priority period and R resources fewer during their low priority period.
+By definition, this alternative allocation is preferred to the real allocation, contradicting Pareto efficiency.
+
+Theorem 2.
+Under realistic conditions, the implementation of DRF in Mesos is not strategy-proof, Pareto efficient, envy-free, or compatible with the sharing incentive.
+DRF satisfies a weaker form of strategy-proofness, ``look-ahead strategy proofness," such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler's future behavior.
+
+Proof: For variety, we consider the case of inhomogeneous resources.
+Again, the proof is identical in any of the given cases.
+For each property we construct a special situation in which DRF fails to achieve that property.
+
+Strategy-proofness: consider the setting where a framework's top priority is achieving some particularly valuable resource X which is currently in use, though they have other tasks which they value less.
+To be most extreme, suppose the user values any outcome in which they receive X higher than any outcome in which they do not.
+A user can arrange to receive X by strategically passing up resource offers which they could use, in order to maximize their probability of being offered the resource X when it first becomes free.
+DRF is only ``strategy-proof" in the sense that a user who anticipates all future behavior of the scheduler will honestly state whether they want a resource in light of the consequences on the scheduler.
+Pareto-efficiency: This is a corollary of the preceding theorem.
+In the case of inhomogeneous resources, suppose that two users have streams of tasks, some of which run faster on resources of type A and some of which run faster on resources of type B.
+Then no demand-based scheduler can ensure that tasks are always placed on the resources on which they run fastest.
+Envy-freeness and compatibility with sharing incentive: Suppose that one user consumes ⅓ of the resources in the cluster and another consumes ½ of the resources, but a particular 10% of the resources in the cluster are several times more valuable (to every user) than they appear.
+This could be based on hardware characteristics to which the scheduler is oblivious.
+The user who consumes ⅓ of the resources receives all resource offers first, and so claims all 10% of these resources.
+But this means that this user receives significantly more total value than the other user, violating both envy-freeness and the sharing incentive.
+
+Theorem 3. The sharing incentive and Pareto efficiency are incompatible for demand-based systems which deal with time-varying demands of varying importance.
+
+Proof: %XXX, Insert proof, it's super straightforward]
+\subsection{Virtues of economic scheduling}
+In this section, we show that our system possesses weaker versions of the theoretical guarantees of the theoretical properties that have been ascribed to existing schedulers.
+In light of the arguments in the preceding section, we hope to illustrate that the two systems are on comparable theoretical footings.
+
+The first theorem considers the setting in which user's willingness to pay [XXX continue]
+
+Theorem 4.
+[Sharing incentive] Each user A values the total resources they receive at least as much as they value their share of the cluster (i.e.
+the amount paid by A divided by the entire cost paid by all users of the cluster).
+
+Proof: Consider a particular user A. During any auction, let $p_A$ be the price that $A$ pays, 
+let $p_B$ be the price paid by all other users, let $R_A$ be the resources received by A, and let $R_B$ be the resources received by all other users.
+The key point is that user A values $R_A$ at at least $p_A$, and values $R_B$ at at most $p_B$.
+Thus user A values their share of the resources at at least $\frac {p_A}{p_A + p_B}$.
+
+%XXX finish proof, very easy.
+
+Theorem 5.
+Using a closed currency, if the rate of income of a particular user is p, that user can adopt a bidding strategy which ensures that they receive a p fraction of the cluster during any period of length T, where T is an upper bound for the length of a task (i.e.
+the maximum of the minimum amount of time after which any task can be revoked).
+
+Proof:
+
+\begin{table*}[t!]
+\begin{center}
+    \begin{tabular}{| l | l | l | l | l | l |}
+    \hline
+    Desired & \small DRF & \small DRF & \small Market-based  & something & something\\
+    Properties & \small(simple) & \small (complex) & \small Mechanism  & something & something\\
+    \hline
+    \small Envy-Freeness & \cmark & \cmark  & \cmark & \cmark   & \cmark\\
+    \small Pareto-Efficiency & 5 & 6  & 4  & \cmark  & \cmark\\
+    \small Resource Monotonicity & 8 & 9  & 4  & \cmark  & \cmark \\
+    7 & 8 & 9  & 4  & \cmark  & \cmark \\
+    7 & 8 & 9  & 4  & \cmark  & \cmark\\
+    7 & 8 & 9  & 4 & \cmark  & \cmark\\
+    \hline
+    \end{tabular}
+\end{center}
+  \caption{A simple table}
+  \label{table:props}
+\end{table*}
+
 \section{Experimental Evaluation}
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{images/util_high.png}
+\caption{Utilization achieved by DRF and our policy on a simulated 25-node CPU-bound cluster.  DRF's average utilization is 98\% average utilization while ours is 99\%.}
+\label{img:util_high}
+\end{figure}
+
+\begin{figure}
+
+\includegraphics[width=0.5\textwidth]{images/util_low.png}
+\caption{Behavior of DRF and our policy on a simulated 100-node cluster. Both policies have average utilization of 44\%.}
+\label{img:util_low}
+\end{figure}
+
 Currently, Mesos jobs and tasks are not attached to economic indicators, since DRF does not rely on any economic-based resource scheduler.
@@
 
-Figures CPU-UTILIZATION and RAM-UTILIZATION show the CPU and RAM utilizations of DRF and the market-based mechanism in the high contention environment.
-As noted, the Google traces indicated cluster jobs were primarily CPU-bound, and hence the cluster witnesses near-maximal CPU utilization but lower RAM utilization.
-Figure CPU-UTILIZATION indicates that the utilization achieved by DRF and the default bidding policy are nearly identical.
+Figure \ref{img:util_high} shows the CPU utilizations of DRF and the market-based mechanism in the high contention environment.
+The utilizations achieved by DRF and the default bidding policy are nearly identical.
 The average DRF utilization is approximately 98\%, while the market-based mechanism is approximately 99\%.
 Note the graph begins after 10 hours, when consistent maximum contention is reached.
-Figure RAM-UTILIZATION depicts the memory utilization, showing again the similar performance between DRF and the market-based mechanism.
-DRF's average memory utilization is TODO\%, while the market-based mechanism's average memory utilization is TODO\%.
-We do not show the disk utilization because very few jobs in the Google traces used local disk space (presumably instead relying on the Google File System).
+We elide the memory utilizations graph because it is not under high contention, as the Google traces indicate jobs are CPU bound, and looks similarly to Figure \ref{img:util_low}.
+However, it shows again the nearly identical performance between DRF and the market-based mechanism.
+Similarly, we do not show the disk utilization because very few jobs in the Google traces used local disk space (presumably instead relying on a Google-internal reliable file system).
 
-Figure CPU-UTILIZATION-LOW shows the CPU utilizations of DRF and the market-based mechanism in a low contention environment, when no resource is fully utilized.
+Figure \ref{img:util_low} shows the CPU utilizations of DRF and the market-based mechanism in a low contention environment, when no resource is fully utilized.
 As we can see, DRF and the market-based mechanism perform nearly identical.
 Both policies have an average CPU utilization of 44\%.
-We elide the memory and disk utilization figures because they repeat the same story, but are less interesting due to the lower RAM and disk resource requirements of jobs.
+Again, we omit the memory and disk utilizations figures because they repeat the same story, but are less interesting due to the lower RAM and disk resource requirements of jobs.
 
-Finally, Figure JOB-COMPLETION displays the progression of workload completion under both scheduling policies.
-When all tasks of a job are completed, the job is considered finished.
-The graph shows the fraction of complete jobs as time progresses.
-Again, both policies result in similar behaviour, completing the workload in nearly identical fashion.
+Finally, Figure \ref{img:reg_fairness} displays the split-wise share of cluster resources each of the five frameworks are allocated in the market-based mechanism.
+Under high contention, all five frameworks have queued tasks to run, and we see that each framework gets roughly a fifth of the cluster resources.
+This indicates the market-based mechanism allocates resources fairly , similar to DRF.
 
 All of these results are gathered when the market-based mechanism uses a default bidding policy because the job requests provide no economic information.
-This shows that the market-based mechanism is ``backwards-compatible" by providing comparable performance to DRF when pricing information is not used.
+This shows that the market-based mechanism is ``backwards-compatible" by providing comparable utilization and fairness performances to DRF when pricing information is not used.
 This result is not completely surprising though, because the default bidding policy behaves similarly to DRF.
@@
 
-Figure JOB-COMPLETION depicts the time progression of job completions, where a job is considered finished when all of its tasks are finished.
+Figure \ref{img:inhomo} depicts the time progression of job completions, where a job is considered finished when all of its tasks are finished.
 As the figure depicts, the market-based mechanism is consistently ahead of DRF at all times, and finishes all jobs in about 20\% less time than DRF.
@@
 By better scheduling jobs on machines that best complete them, we see the overall performance improvements of the market-based mechanism.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{images/inhomo_times.png}
+\caption{The results of simulating Mesos on a cluster of 64 machines, of which 16 have access to a special resource.
+DRF schedules 30\% of tasks on the optimal machine when frameworks prioritize appropriately, while a simple market-based policy schedules 60\%.}
+\label{img:inhomo}
+\end{figure}
 

### 2013-12-18 paper/paper.tex
Filling out more sections

@@
 \begin{abstract}
-
+Current cluster managers arbitrate complex and possibly conflicting user requirements through a fairness criterion such as dominant resource fairness.
+However, in realistic settings, these approaches fail to be both efficient and non-manipulable.
+In this paper, we propose using prices as a method of expressing user constraints, and describe a market-based mechanism for allocating resources in a cluster.
+We demonstrate that our approach achieves desirable theoretical properties, such as envy-freeness and compatibility with sharing incentives.
+We incorporate our mechanism into the design of the Mesos cluster scheduler, and show through simulations that our modifications result in comparable or better performance characteristics when compared with the existing Mesos framework.
+In particular, our scheme can match Mesos's dominant resource fairness's performance when even no economic information is provided.
+When economic information is provided, our mechanism provides performance improvements.
 \end{abstract}
@@
 allocating these resources to users with competitive and potentially
-incompatible demands. Such conflicts are typically arbitrated \emph{fairness}
-criterions, such as dominant resource fairness (DRF), which benefit from their
+incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
+criterions, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
 simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
-realistic settings---when dealing with inhomogeneous resources, time-varying
+realistic settings --- when dealing with inhomogeneous resources, time-varying
 demands, requirements for data locality, etc.---these systems cease to be either
@@
 
-We implement these ideas in the Mesos cluster manager, along with microeconomic
+We incorporate these ideas into the Mesos cluster manager, along with microeconomic
 ``agents'' which allow traditional Mesos clients to interact seamlessly with our
-modified implementation. We show that the computational and communication
-overhead proposed by our system is manageable and that its performance compares
-favorably to existing approaches (particularly DRF) even when users do not
+modified implementation.
+We show through simulations that our market-based mechanism has performance characteristics similar or better compared to existing approaches (in particular, DRF) even when users do not
 provide any meaningful price information. Moreover, we show that when accurate
-economic data is available our system is able to achieve substantially higher
-social welfare than DRF. Finally, we discuss a number of examples where this
+economic data is available our system is able to achieve substantial
+performance improvements over DRF. Finally, we discuss a number of examples where this
 functionality may be useful even in applications where the end-users of the
@@
 
-\subsection{Guide to the paper}
-
-In section \ref{sec:overview}, we provide a brief overview of Mesos and how it
+The rest of the paper is organized as follows.
+Section \ref{sec:overview} provides a brief overview of Mesos and how it
 could incorporate microeconomic mechanisms.
-
-In section \ref{sec:case}, we make the theoretical case for using microeconomic methods. We
-provide a litany of examples in which existing approaches, and in particular
-DRF, fail to be either efficient or strategy-proof, and describe examples of
-strategic behavior in Mesos. We discuss a number of examples in which economic
-data generated \emph{within} the system could be useful, and compare this approach to a
-number of ad hoc approaches currently pursued to solve similar problems.
-
-In section \ref{sec:design}, we describe our protocol and the most important design decisions
+%
+%In section \ref{sec:case}, we make the theoretical case for using microeconomic methods. We
+%provide a litany of examples in which existing approaches, and in particular
+%DRF, fail to be either efficient or strategy-proof, and describe examples of
+%strategic behavior in Mesos. We discuss a number of examples in which economic
+%data generated \emph{within} the system could be useful, and compare this approach to a
+%number of ad hoc approaches currently pursued to solve similar problems.
+%
+In Section \ref{sec:design}, we describe our protocol and the most important design decisions
 we made. In particular, we describe the mechanisms we used to ensure that our
@@
 the clients' code.
-
-In section \ref{sec:eval}, we report on simulated comparisons between our
-design and existing approaches: (a) we evaluate the computational and communication
-overhead of our approach and show that it is manageable, (b) we compare our
-system in ``backwards-compatibility mode,'' without any economic information
-whatsoever, to DRF, and show that it performs comparably whether judged by
-utilization or fairness, (c) we examine a number of cases in which economic
-information is available; we show that in general our algorithms achieve higher
-social efficiency than DRF, and provide natural examples in which DRF fails to
-be Pareto efficient.
-
-In section \ref{sec:future}, we elaborate on directions for further
-investigation.
-
-In section \ref{sec:conclusion}, we making closing remarks.
+%
+We provide a theoretical analysis of the shortcomings of DRF and the benefits of an economic-based scheduler in Section \ref{sec:theory}.
+%
+In Section \ref{sec:eval}, we report on simulated performance valuations, comparing our
+design and the existing DRF approach.
+%: (a) we evaluate the computational and communication
+%overhead of our approach and show that it is manageable, (b) we compare our
+%system in ``backwards-compatibility mode,'' without any economic information
+%whatsoever, to DRF, and show that it performs comparably whether judged by
+%utilization or fairness, (c) we examine a number of cases in which economic
+%information is available; we show that in general our algorithms achieve higher
+%social efficiency than DRF, and provide natural examples in which DRF fails to
+%be Pareto efficient.
+Related works are discussed in Section \ref{sec:related}.
+We elaborate on directions for further investigation in Section \ref{sec:future}, and make concluding remarks in Section \ref{sec:conclusion}.
 
@@
 machines that improve data locality), but Mesos itself makes use of a very
-simple fairness criterion to decide which frameworks receive offers.
+simple fairness criterion (dominant resource fairness) to decide which frameworks receive offers.
 
@@
 strategy-proof in a simple one-shot game with homogeneous resources, it is
-neither efficient nor strategy-proof in this setting. For example, a framework
-using Mesos which prefers to run tasks on machines that already have relevant
-data is forced to engage in strategic behavior: given a resource which it
-\emph{could} use now, should it take the resource or decline it, so that it
-might receive a better offer in the future? Solutions to this problem rely on
-simple heuristics which require tuning based on the parameters of the system;
-there are simple examples where the resulting allocations are not efficient
-despite best-efforts of the clients, and in complex examples there is little to
-believe the results are efficient. Moreover, despite being ``strategy-proof'' the
+neither efficient nor strategy-proof in this setting. 
+%For example, a framework
+%using Mesos which prefers to run tasks on machines that already have relevant
+%data is forced to engage in strategic behavior: given a resource which it
+%\emph{could} use now, should it take the resource or decline it, so that it
+%might receive a better offer in the future? Solutions to this problem rely on
+%simple heuristics which require tuning based on the parameters of the system;
+%there are simple examples where the resulting allocations are not efficient
+%despite best-efforts of the clients, and in complex examples there is little to
+%believe the results are efficient. 
+Moreover, the
 current design of Mesos is essentially unsuitable for even mildly hostile
-environments; a framework which can use less than its ``fair share'' of the
-resources at any point in time has no incentive to do so, and indeed has every
-incentive to exploit all resources it can be allocated even if they are being
-used arbitrarily inefficiently (and there is always \emph{something} to do with
-idle resources, if only perform proof-of-work in exchange for small amounts of
-money).
+environments. Section \ref{sec:theory} provides detailed theoretical analyses.
+%; a framework which can use less than its ``fair share'' of the
+%resources at any point in time has no incentive to do so, and indeed has every
+%incentive to exploit all resources it can be allocated even if they are being
+%used arbitrarily inefficiently (and there is always \emph{something} to do with
+%idle resources, if only perform proof-of-work in exchange for small amounts of
+%money).
 
@@
 been considered are:
+\vspace{-4mm}
 \begin{enumerate}
+\itemsep0em
   \item Ignore the relative value of resource $R$ and $R'$, and make allocation
@@
 
-\section{The case for microeconomic scheduling}
-\label{sec:case}
-
-\subsection{Scheduling is hard}
-Consider the following typical situations within a cluster:
-\begin{enumerate}
-  \item Some clients have regular throughput and flexible deadlines, while some
-    clients have hard real-time constraints and variable traffic.
-  \item Different tasks make use of different characteristics of hardware on
-    machines in the cluster, for example high ratios of RAM to CPU on a
-    particular machine, or GPUs or other hardware that is available on only
-    certain machines.
-  \item Tasks require data which is located on disk or even in memory somewhere
-    in the cluster, and co-locating the tasks with the data improves
-    performance.
-\end{enumerate}
-In each of these examples, clients of the cluster have preferences over
-allocations which are difficult to precisely express. It would be possible but
-difficult to cover just these cases, but the reader can doubtless generate many
-similar cases, and as the environment changes the nature of these constraints is
-likely to continue to change as well.
-
-Mesos is able to schedule even in the face of such constraints, by making
-resource offers to clients and allowing them to accept or reject resources
-according to whether they satisfy their constraints. But this is approach offers
-little granularity to clients, forces them to adopt brittle heuristics, and
-moreover compromises the guarantees of the fairness policies Mesos uses to
-decide how to make resource offers.
-
-Mesos uses a fair-share scheduler based on dominant resource fairness. This
-means that the client to receive the next resource offer is the one who is
-currently using the minimum share of the resource they are using the \emph{most}
-of (relative to the total supply in the cluster). A weighted version can be
-defined analogously.
-
-Consider a client of Mesos who is interested in receiving a machine with
-characteristic X, because it would allow their task to run 20\% faster (or
-perhaps because it would allow them to run a task which is slightly higher
-priority than the task they would run on a machine without characteristic X).
-Given an offer for a machine without characteristic X, what should this client
-do? The formal guarantee of ``strategy-proofness'' suggests the client would take
-it; indeed, to do otherwise would explicitly be strategic. But in fact, we hope
-that clients will yield a highly-contended resource when they can use an
-alternative, or will yield a typical resource if they could make particularly
-good use of an alternative. And indeed this is done by many clients to Mesos.
-
-This example clearly shows that in this case, the mechanism provided by Mesos is
-\emph{not} strategy-proof. Worse, it's not Pareto efficient if people are
-honest, and need not be Pareto efficient if clients behave optimally. Similar
-things happen in the other examples we mentioned, or in most of the similar
-alternatives which we can envision:
-\begin{enumerate}
-  \item When one client has a constant stream of work and another has varying
-    traffic, Mesos encourages both to constantly use up their allocated share of
-    the network (unless they have nothing to do with the space). But an
-    efficient allocation would give the client with varying workload more
-    resources when it has more work. 
-  \item Mesos gives a valuable resource to whatever client happens to be using
-    the fewest resources when that machine becomes available. This encourages
-    clients to inefficiently decline resources which they could use, so that
-    they will be offered better resources in the future. This may decrease
-    utilization, and moreover it provides little guarantee that a valuable
-    resource will be used by the framework which most values it---instead it will
-    be used by whichever framework uses the least resources.
-  \item If a client is waiting for a machine that is co-located with some data
-    that their task needs, then Mesos encourages them to guess how likely that
-    resource is to be freed up soon, and to decline new resources if this
-    probability is high enough. This is actually much more efficient behavior
-    than if the client behaved honestly by accepting whatever resources it could
-    use, but it provides some indication that the ``guarantees'' of DRF are not
-    directly applicable to the situations Mesos is intended to cover.
-  \end{enumerate}
-
-These shortcomings are not specific to DRF; these will be issues for any
-scheduler which treats the scheduling problem as a one-shot game with
-homogeneous resources when in fact it is more complicated. Theoretical
-guarantees are not likely to be meaningful in this regime. To evaluate proposed
-solutions, we suggest a combination of:
-\begin{enumerate}
-  \item Theoretical analyses which apply in realistic contexts
-  \item Experimental evidence for effectiveness
-\end{enumerate}
-We provide strong evidence that our proposal is at least not inferior to DRF on
-either of these grounds, and we provide some evidence that even our highly
-preliminary implementation is already superior.
-
-\subsection{Existing approaches}
-Many difficulties with scheduling have been isolated and addressed, typically by
-ad hoc mechanisms which require tuning and don't necessarily play nicely with
-each other. In order to contrast these approaches with microeconomic methods, we
-list some examples of solutions to these problems here. Note that we will not be
-able to solve all of these problems within our proposal---that would be an
-extraordinarily ambitious project. We list these examples to give some sense of
-how a microeconomic framework could be used to replace ad hoc approaches,
-improving robustness and ease-of-design. In contrast, our goal in this paper is
-simply to show that microeconomic approaches really are a feasible option, and
-that in the ``base case'' they are as good as existing solutions.
-
-\paragraph{Deadlines} DRF makes no provision for coping with deadlines, which
-are often of considerable practical importance. The Jockey system enforces
-deadlines in the context of a fair-share scheduler, by increasing or decreasing
-a task's share of the cluster depending on the importance of their deadline.
-While this is a significant improvement over the alternative, we find it a very
-crude solution to the underlying problem:
-\begin{enumerate}
-  \item Jockey has no dependence on how important resources currently are for
-    the cluster, it just assigns a job as many resources as are needed to meet
-    its deadline.
-  \item It is not clear how to generalize Jockey to systems where multiple
-    simultaneous tasks have deadlines, or where meeting deadlines must be
-    balanced against any other consideration.
-  \item Jockey changes the allocations of tasks depending on their performance,
-    and will typically invalidate any guarantees provided by the original
-    scheduler.
-  \item Jockey does not have any principled approach for reasoning about the
-    error bars on a task's completion time (instead this is determined by a
-    fine-tuned parameter of the system).
-  \item Jockey cannot reason about multiple deadlines of varying importance, but
-    instead gives a job as many resources as it needs to finish as soon as it
-    would be useful.
-\end{enumerate}
-
-The microeconomic alternative makes use of Jockey's core component, an estimate
-for the time required to complete a task, but uses a different control system.
-In the microeconomic framework a deadline is associated with an economic value
-(that might be algorithmically generated based on the priority of the task)
-which can be compared to the economic value of other activity in the cluster.
-The importance of resources to the task is then given by the effect those
-resources will have on the task's probability of completing by deadline, and
-this can be compared to the importance of those resources to other processes
-running on the cluster. Resources can then be shifted until these two values are
-equal.
-
-\paragraph{Priority and preemption} In existing systems priority is typically
-implemented as an absolute ordering; a task of high priority can preempt a task
-of lower priority and always wins in contention for resources. This approach is
-conceptually problematic because there are always mechanisms for a
-higher-priority process to improve performance by increasing its resource usage
-(for example speculative execution, or increased duplication of straggling
-processes) and an infinite tradeoff between the performance of high-priority and
-low-priority processes is undesirable. In practice, this approach relies on
-``reasonable'' behavior by high-priority processes, which makes reasoning about
-systems difficult. Such systems are also brittle and prone to priority
-inversions, in which low-priority processes can be inadvertently elevated to
-high-priority.
-
-Another approach is to assign tasks of different types appropriate shares of a
-cluster. But this approach also fails to capture what we really care about. For
-example, we would like high priority processes to expand their use of the
-cluster when they need it.
-
-These problems are considerably exacerbated when we consider preemption,
-especially if preemption is costly for the preempted process: when should a low
-priority process be allowed to finish, and when should it be preempted?
-
-Microeconomic methods allow for a principled answer to these questions: by
-describing ``high priority'' tasks by \emph{how much more} we care about them
-finishing faster, we can make principled tradeoffs.
-
-\paragraph{Data locality} Many tasks run more efficiently when they are
-co-located with data. At the moment, this is typically achieved either by
-explicit optimization (requiring the scheduler to be aware of detailed
-characteristics of the tasks its scheduling) or by heuristics, for example
-blocking for 5 seconds before accepting an offered resource which is not local
-to data. Again, microeconomic methods provide a principled approach which is
-compatible with a lightweight interface between client and scheduler: a client
-can estimate how much more slowly a task will run on a machine without the data,
-can estimate how likely a machine with the data is to become free, and can
-thereby estimate how much of a discount they would need to be offered before
-they would accept a machine without their data.
-
-\subsection{Philosophical motivation}
-Our primary motivation is strongly to maximize efficiency, rather than other
-measures such as utilization, fairness, or strategy-proofness. We view other
-characteristics as necessary insofar as they help achieve efficiency.
-
-In some sense this is problematic, because efficiency is typically unmeasurable.
-But there are a number of pragmatically relevant implications:
-\begin{enumerate}
-  \item Pareto efficiency is a minimal standard for acceptability. To the extent
-    that existing approaches fail to be Pareto efficient, this is much more
-    damning than a possible failure to be strategy-proof (as long as the
-    possibility of manipulation does not in itself destroy our efficiency
-    guarantee!)
-  \item Even where true prices are unavailable, we think in terms of the real,
-    unobserved value of an outcome (such as finishing a computation or meeting a
-    deadline). Many existing schemes need to implicitly make judgments about
-    these values (because they are making tradeoffs between different outcomes).
-    So we don't treat the difficulty of assigning values to outcomes as a
-    deal-breaker; to the extent that we already need to make implicit tradeoffs,
-    reifying those tradeoffs is only likely to help us improve the situation.
-\end{enumerate}
+%\section{The case for microeconomic scheduling}
+%\label{sec:case}
+%
+%\subsection{Scheduling is hard}
+%Consider the following typical situations within a cluster:
+%\begin{enumerate}
+%  \item Some clients have regular throughput and flexible deadlines, while some
+%    clients have hard real-time constraints and variable traffic.
+%  \item Different tasks make use of different characteristics of hardware on
+%    machines in the cluster, for example high ratios of RAM to CPU on a
+%    particular machine, or GPUs or other hardware that is available on only
+%    certain machines.
+%  \item Tasks require data which is located on disk or even in memory somewhere
+%    in the cluster, and co-locating the tasks with the data improves
+%    performance.
+%\end{enumerate}
+%In each of these examples, clients of the cluster have preferences over
+%allocations which are difficult to precisely express. It would be possible but
+%difficult to cover just these cases, but the reader can doubtless generate many
+%similar cases, and as the environment changes the nature of these constraints is
+%likely to continue to change as well. 
+%
+%Mesos is able to schedule even in the face of such constraints, by making
+%resource offers to clients and allowing them to accept or reject resources
+%according to whether they satisfy their constraints. But this is approach offers
+%little granularity to clients, forces them to adopt brittle heuristics, and
+%moreover compromises the guarantees of the fairness policies Mesos uses to
+%decide how to make resource offers.
+%
+%Mesos uses a fair-share scheduler based on dominant resource fairness. This
+%means that the client to receive the next resource offer is the one who is
+%currently using the minimum share of the resource they are using the \emph{most}
+%of (relative to the total supply in the cluster). A weighted version can be
+%defined analogously. 
+%
+%Consider a client of Mesos who is interested in receiving a machine with
+%characteristic X, because it would allow their task to run 20\% faster (or
+%perhaps because it would allow them to run a task which is slightly higher
+%priority than the task they would run on a machine without characteristic X).
+%Given an offer for a machine without characteristic X, what should this client
+%do? The formal guarantee of ``strategy-proofness'' suggests the client would take
+%it; indeed, to do otherwise would explicitly be strategic. But in fact, we hope
+%that clients will yield a highly-contended resource when they can use an
+%alternative, or will yield a typical resource if they could make particularly
+%good use of an alternative. And indeed this is done by many clients to Mesos.
+%
+%This example clearly shows that in this case, the mechanism provided by Mesos is
+%\emph{not} strategy-proof. Worse, it's not Pareto efficient if people are
+%honest, and need not be Pareto efficient if clients behave optimally. Similar
+%things happen in the other examples we mentioned, or in most of the similar
+%alternatives which we can envision:
+%\begin{enumerate}
+%  \item When one client has a constant stream of work and another has varying
+%    traffic, Mesos encourages both to constantly use up their allocated share of
+%    the network (unless they have nothing to do with the space). But an
+%    efficient allocation would give the client with varying workload more
+%    resources when it has more work. 
+%  \item Mesos gives a valuable resource to whatever client happens to be using
+%    the fewest resources when that machine becomes available. This encourages
+%    clients to inefficiently decline resources which they could use, so that
+%    they will be offered better resources in the future. This may decrease
+%    utilization, and moreover it provides little guarantee that a valuable
+%    resource will be used by the framework which most values it---instead it will
+%    be used by whichever framework uses the least resources.
+%  \item If a client is waiting for a machine that is co-located with some data
+%    that their task needs, then Mesos encourages them to guess how likely that
+%    resource is to be freed up soon, and to decline new resources if this
+%    probability is high enough. This is actually much more efficient behavior
+%    than if the client behaved honestly by accepting whatever resources it could
+%    use, but it provides some indication that the ``guarantees'' of DRF are not
+%    directly applicable to the situations Mesos is intended to cover.
+%  \end{enumerate}
+%
+%These shortcomings are not specific to DRF; these will be issues for any
+%scheduler which treats the scheduling problem as a one-shot game with
+%homogeneous resources when in fact it is more complicated. Theoretical
+%guarantees are not likely to be meaningful in this regime. To evaluate proposed
+%solutions, we suggest a combination of:
+%\begin{enumerate}
+%  \item Theoretical analyses which apply in realistic contexts
+%  \item Experimental evidence for effectiveness
+%\end{enumerate}
+%We provide strong evidence that our proposal is at least not inferior to DRF on
+%either of these grounds, and we provide some evidence that even our highly
+%preliminary implementation is already superior.
+%
+%\subsection{Existing approaches}
+%Many difficulties with scheduling have been isolated and addressed, typically by
+%ad hoc mechanisms which require tuning and don't necessarily play nicely with
+%each other. In order to contrast these approaches with microeconomic methods, we
+%list some examples of solutions to these problems here. Note that we will not be
+%able to solve all of these problems within our proposal---that would be an
+%extraordinarily ambitious project. We list these examples to give some sense of
+%how a microeconomic framework could be used to replace ad hoc approaches,
+%improving robustness and ease-of-design. In contrast, our goal in this paper is
+%simply to show that microeconomic approaches really are a feasible option, and
+%that in the ``base case'' they are as good as existing solutions.
+%
+%\paragraph{Deadlines} DRF makes no provision for coping with deadlines, which
+%are often of considerable practical importance. The Jockey system enforces
+%deadlines in the context of a fair-share scheduler, by increasing or decreasing
+%a task's share of the cluster depending on the importance of their deadline.
+%While this is a significant improvement over the alternative, we find it a very
+%crude solution to the underlying problem:
+%\begin{enumerate}
+%  \item Jockey has no dependence on how important resources currently are for
+%    the cluster, it just assigns a job as many resources as are needed to meet
+%    its deadline.
+%  \item It is not clear how to generalize Jockey to systems where multiple
+%    simultaneous tasks have deadlines, or where meeting deadlines must be
+%    balanced against any other consideration.
+%  \item Jockey changes the allocations of tasks depending on their performance,
+%    and will typically invalidate any guarantees provided by the original
+%    scheduler.
+%  \item Jockey does not have any principled approach for reasoning about the
+%    error bars on a task's completion time (instead this is determined by a
+%    fine-tuned parameter of the system).
+%  \item Jockey cannot reason about multiple deadlines of varying importance, but
+%    instead gives a job as many resources as it needs to finish as soon as it
+%    would be useful.
+%\end{enumerate}
+%
+%The microeconomic alternative makes use of Jockey's core component, an estimate
+%for the time required to complete a task, but uses a different control system.
+%In the microeconomic framework a deadline is associated with an economic value
+%(that might be algorithmically generated based on the priority of the task)
+%which can be compared to the economic value of other activity in the cluster.
+%The importance of resources to the task is then given by the effect those
+%resources will have on the task's probability of completing by deadline, and
+%this can be compared to the importance of those resources to other processes
+%running on the cluster. Resources can then be shifted until these two values are
+%equal.
+%
+%\paragraph{Priority and preemption} In existing systems priority is typically
+%implemented as an absolute ordering; a task of high priority can preempt a task
+%of lower priority and always wins in contention for resources. This approach is
+%conceptually problematic because there are always mechanisms for a
+%higher-priority process to improve performance by increasing its resource usage
+%(for example speculative execution, or increased duplication of straggling
+%processes) and an infinite tradeoff between the performance of high-priority and
+%low-priority processes is undesirable. In practice, this approach relies on
+%``reasonable'' behavior by high-priority processes, which makes reasoning about
+%systems difficult. Such systems are also brittle and prone to priority
+%inversions, in which low-priority processes can be inadvertently elevated to
+%high-priority.
+%
+%Another approach is to assign tasks of different types appropriate shares of a
+%cluster. But this approach also fails to capture what we really care about. For
+%example, we would like high priority processes to expand their use of the
+%cluster when they need it. 
+%
+%These problems are considerably exacerbated when we consider preemption,
+%especially if preemption is costly for the preempted process: when should a low
+%priority process be allowed to finish, and when should it be preempted?
+%
+%Microeconomic methods allow for a principled answer to these questions: by
+%describing ``high priority'' tasks by \emph{how much more} we care about them
+%finishing faster, we can make principled tradeoffs. 
+%
+%\paragraph{Data locality} Many tasks run more efficiently when they are
+%co-located with data. At the moment, this is typically achieved either by
+%explicit optimization (requiring the scheduler to be aware of detailed
+%characteristics of the tasks its scheduling) or by heuristics, for example
+%blocking for 5 seconds before accepting an offered resource which is not local
+%to data. Again, microeconomic methods provide a principled approach which is
+%compatible with a lightweight interface between client and scheduler: a client
+%can estimate how much more slowly a task will run on a machine without the data,
+%can estimate how likely a machine with the data is to become free, and can
+%thereby estimate how much of a discount they would need to be offered before
+%they would accept a machine without their data.
+%
+%\subsection{Philosophical motivation}
+%Our primary motivation is strongly to maximize efficiency, rather than other
+%measures such as utilization, fairness, or strategy-proofness. We view other
+%characteristics as necessary insofar as they help achieve efficiency. 
+%
+%In some sense this is problematic, because efficiency is typically unmeasurable.
+%But there are a number of pragmatically relevant implications:
+%\begin{enumerate}
+%  \item Pareto efficiency is a minimal standard for acceptability. To the extent
+%    that existing approaches fail to be Pareto efficient, this is much more
+%    damning than a possible failure to be strategy-proof (as long as the
+%    possibility of manipulation does not in itself destroy our efficiency
+%    guarantee!)
+%  \item Even where true prices are unavailable, we think in terms of the real,
+%    unobserved value of an outcome (such as finishing a computation or meeting a
+%    deadline). Many existing schemes need to implicitly make judgments about
+%    these values (because they are making tradeoffs between different outcomes).
+%    So we don't treat the difficulty of assigning values to outcomes as a
+%    deal-breaker; to the extent that we already need to make implicit tradeoffs,
+%    reifying those tradeoffs is only likely to help us improve the situation.
+%\end{enumerate}
 
@@
 propose:
+\vspace{-5mm}
 \begin{enumerate}
+\itemsep0em
   \item Estimate the value of different outcomes.
@@
 \end{enumerate}
-
+\vspace{-5mm}  
 This paradigm has the virtue of being modular in a number of important respects:
+\vspace{-5mm}
 \begin{enumerate}
+\itemsep0em
   \item The notion of value provides a unifying framework for different
@@
 \section{Market-based Mechanism Design}
+
+This section describes the details of our market-based mechanism design.
+
 \label{sec:design}
@@
 \section{Theoretical analysis}
+\label{sec:theory}
 
@@
 \section{Related Work}
+\label{sec:related}
+
 \subsection{Grid computing}
@@
 \subsection{Resource allocation}
-Dominant resource fairness~\cite{drf}
+Dominant resource fairness~\cite{drf} is an allocation policy whereby the user with the smallest dominant share is next allocated resources.
+The user's dominant share in a multi-resource environment is the largest share the user possesses of any of the cluster's various resources.
 
@@
 
-\section{Discussion and Future Work}
+\section{Future Work}
 \label{sec:future}
+
+In our evaluation, we showed through simulation the benefits of our protocol in the specific case of inhomogenous performing resources.
+However, there are a number of other user constraints that should theoretically be better expressed using prices than existing methods.
+Future work would be to experimentally evaluate such cases.
+A few such user constraints include deadlines and varying latency sensitivities, differential service guarantees, deadweight losses of evictions, costs of fragmenting jobs, various execution types (e.g.
+speculative vs essential execution), and co-location of data or other important resources.
 
@@
 \label{sec:conclusion}
+
+This paper presented an initial investigation into the possibility of leveraging prices and a market-based mechanism for resource scheduling.
+We describe a protocol for use in the Mesos cluster scheduler with beneficial theoretical properties.
+Simulation evaluation shows that our market-based mechanism can perform reasonably in a backwards-compatible mode, where no economic information is provided.
+When economic data exists, our approach can provide substantial performance benefits.
 

### 2013-12-18 paper/paper.tex
Adding fairness job completion graph and description

@@
 
+\begin{figure}
+
+\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
+\caption{Relative average job completion times between DRF and auctions for all frameworks.}
+\label{img:relative}
+\end{figure}
+
 Currently, Mesos jobs and tasks are not attached to economic indicators, since DRF does not rely on any economic-based resource scheduler.
@@
 
-Finally, Figure \ref{img:reg_fairness} displays the split-wise share of cluster resources each of the five frameworks are allocated in the market-based mechanism.
-Under high contention, all five frameworks have queued tasks to run, and we see that each framework gets roughly a fifth of the cluster resources.
-This indicates the market-based mechanism allocates resources fairly , similar to DRF.
+Finally, Figure \ref{img:relative} displays the relative average job completion time between DRF and the market-based mechanism for the five frameworks.
+As we see, the ratio is roughly 1.0 for all frameworks, which indicates the market-based mechanism is roughly as fair as DRF, and that jobs complete at the same approximate rate.
 

### 2013-12-18 paper/paper.tex
Inserted theory section to paper

@@
 % For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{acm_proc_article-sp}
 
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+
+\newenvironment{pproof}[1][Proof]{\begin{trivlist}
+\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+%\newenvironment{definition}[1][Definition]{\begin{trivlist}
+%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+%\newenvironment{example}[1][Example]{\begin{trivlist}
+%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+%\newenvironment{remark}[1][Remark]{\begin{trivlist}
+%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+
+%\newcommand{\qed}{\nobreak \ifvmode \relax \else
+%      \ifdim\lastskip<1.5em \hskip-\lastskip
+%      \hskip1.5em plus0em minus0.5em \fi \nobreak
+%      \vrule height0.75em width0.5em depth0.25em\fi}
+
+\usepackage{amsmath}
 \usepackage{mathtools}
@@
 Within our setting, the framework must associate a willingness to pay with each
-task it wishes to run. We now describe some reasonable ways for the frameworks
-to do so.
-
-\paragraph{Default policy} For backwards compatibility, we want to be able to
+task it wishes to run.
+
+\paragraph{Default policy} For backwards compatibility, 
+and as a starting point for designing more complex policies, we want to be able to
 use existing Mesos frameworks which are not aware of prices. For these, we
@@
 
+Formally, each framework calculates the current net present value
+of their accumulated wealth together with their current obligations
+and stream of income, and then bids a price proportional
+to this total. This guarantees that the frameworks will
+maintain roughly equal budgets (and hence use roughly equal shares
+of the cluster), since any framework which became richer
+than the others would begin winning auctions.
+
+\paragraph{Paying more or less} To modify the 
+default policy to accomodate inhomogeneous resources,
+times, or tasks, we can simply modify framework's
+bids to adjust for the desirability of the resource being
+purchased or the importance of the purpose they are being used for.
+
+For example, if a task will take less time when run on a machine
+which already has relevant data loaded into memory,
+a framework can increase its willingness to pay for resources on that machine
+by an amount depending on the anticipated speedup.
+%XXX mention why we don't care about any properties other than those that we mention
+
+\paragraph{Defensive bidding} One negative consequence of using a closed economy,
+in which the frameworks bid using currency which is entirely internal to the cluster,
+%XXX mention this distinction elsewhere, and the fact that we can do either
+is the possibility of \emph{hoarding}, in which one framework
+declines to use any resources during a certain period so that it can amass
+a much larger budget than any other resources.
+It can then spend this budget at a future point in order to monopolize the cluster,
+which may have undesirable conseuqences for frameworks that need uninterrupted service.
+
+This can be prevented by using an appropriate bidding strategy
+(in general we recommend modifying bidding strategies to achieve a desired
+function whenever possible and leaving the scheduler itself as simple as possible).
+A defensive bidder $A$ who receives an income equal to a $p$ fraction
+of the cluster's resources can ensure the following invariant:
+during any window of length $T$, $A$ spends roughly $p$ times the total amount
+spent by all frameworks, and at every point in time $A$'s reserves are roughly equal to $p$
+times the total reserves of all frameworks (where $T$ is an upper bound on how frequently auctions are conducted,
+either the maximum length of a task or the period of time after which the resources used by a task
+will be reauctioned and potentially revoked).
+In fact the second invariant follows from the first, which can be approximately attained
+by simply scaling all bids during an interval of time $T$ to the appropriate level.
+
 \section{Theoretical analysis}
@@
 
-\subsection{Drawbacks of non-economic scheduling}
+Theoretical analysis
+Drawbacks of non-economic scheduling
 Most scheduling policies used in practice do not use any economic information: clients request resources, and schedulers allocate those resources.
@@
 
-We will use the suggestive term ``realistic conditions" to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
+We will use the suggestive term “realistic conditions” to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
 
@@
 
-We say that a system is ``demand-based" if it elicits a demand from each user and makes assignments on the basis of the stated demands.
+We say that a system is “demand-based” if it elicits a demand from each user and makes assignments on the basis of the stated demands.
 For example, DRF, asset allocation, and CEEI all fall into this class.
 
-Theorem 1. Any demand-based system which is Pareto efficient under realistic conditions must sometimes assign the entire cluster to a single user, an extreme violation of fairness.
-
-Proof: We provide the proof for the time-varying demands case.
+\begin{theorem}\label{demand-bad}
+Any demand-based system which is Pareto efficient under realistic conditions must sometimes assign the entire cluster to a single user, an extreme violation of fairness.
+\end{theorem}
+
+\begin{pproof}
+We provide the proof for the time-varying demands case.
 The other arguments are exactly analogous.
@@
 
-Suppose that there are two users and that at each time each user has enough tasks to consume all of the clusters' resources.
+Suppose that there are two users and that at each time each user has enough tasks to consume all of the clusters’ resources.
 Tasks arrive at multiples of time T and last for T rounds.
-Moreover, suppose that during each interval of time T each user has an independently and uniformly randomly generated priority which is either ``high" or ``low." The only characteristic of these priorities is that, all else equal, they would prefer run one extra high priority task at the expense of one fewer low priority task.
-
-Since the scheduler is demand-based and the user's priority levels are changing across time, the allocation must be independent of the priority of the users.
-So if each user receives a non-zero share of the resources, then each user must receive a non-zero share of the resources while they are in the ``high" priority state and the other user is in the ``low" priority state.
+Moreover, suppose that during each interval of time T each user has an independently and uniformly randomly generated priority which is either “high” or “low.” The only characteristic of these priorities is that, all else equal, they would prefer run one extra high priority task at the expense of one fewer low priority task.
+
+Since the scheduler is demand-based and the user’s priority levels are changing across time, the allocation must be independent of the priority of the users.
+So if each user receives a non-zero share of the resources, then each user must receive a non-zero share of the resources while they are in the “high” priority state and the other user is in the “low” priority state.
 
@@
 By definition, this alternative allocation is preferred to the real allocation, contradicting Pareto efficiency.
-
-Theorem 2.
+\qed
+\end{pproof}
+
+\begin{theorem}
 Under realistic conditions, the implementation of DRF in Mesos is not strategy-proof, Pareto efficient, envy-free, or compatible with the sharing incentive. 
-DRF satisfies a weaker form of strategy-proofness, ``look-ahead strategy proofness," such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler's future behavior.
+\end{theorem}
+
+DRF satisfies a weaker form of strategy-proofness which we call ``local strategy-proofness,'' 
+such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler’s future behavior. 
+This differs from the ordinary notion in that a user may need to reason strategically about future rounds of allocation in order to determine
+their demand, rather than honestly reporting their real demand.
+%XXX replace user by framework
+%XXX fold this into the clearer general discussion of loca guarantees
 
@@
 
-Strategy-proofness: consider the setting where a framework's top priority is achieving some particularly valuable resource X which is currently in use, though they have other tasks which they value less.
-To be most extreme, suppose the user values any outcome in which they receive X higher than any outcome in which they do not.
-A user can arrange to receive X by strategically passing up resource offers which they could use, in order to maximize their probability of being offered the resource X when it first becomes free.
-DRF is only ``strategy-proof" in the sense that a user who anticipates all future behavior of the scheduler will honestly state whether they want a resource in light of the consequences on the scheduler.
-Pareto-efficiency: This is a corollary of the preceding theorem.
+\begin{itemize}
+\item \textbf{Strategy-proofness:} consider the setting where a framework’s top priority is achieving some particularly valuable resource X 
+which is currently in use, though they have other tasks which they value less. To be most extreme, suppose the user values any outcome in which they receive X 
+higher than any outcome in which they do not. 
+A user can arrange to receive X by strategically passing up resource offers which they could use, in order to maximize 
+their probability of being offered the resource X when it first becomes free. 
+\item \textbf{Pareto-efficiency:} This is a corollary of theorem~\ref{demand-bad}. 
 In the case of inhomogeneous resources, suppose that two users have streams of tasks, some of which run faster on resources of type A and some of which run faster on resources of type B. 
 Then no demand-based scheduler can ensure that tasks are always placed on the resources on which they run fastest.
-Envy-freeness and compatibility with sharing incentive: Suppose that one user consumes ⅓ of the resources in the cluster and another consumes ½ of the resources, but a particular 10% of the resources in the cluster are several times more valuable (to every user) than they appear.
+\item \textbf{Envy-freeness and compatibility with sharing incentive:} Suppose that one user consumes $\frac 13$ of the resources in the cluster and another consumes $\frac 12$ of the resources, 
+but a particular $frac 1{10}$ of the resources in the cluster are $10$ times more valuable (to every user) than they appear. 
 This could be based on hardware characteristics to which the scheduler is oblivious. 
-The user who consumes ⅓ of the resources receives all resource offers first, and so claims all 10% of these resources.
+The user who consumes $\frac 13$ of the resources receives all resource offers first, and so claims all of the especially valuable resources. 
 But this means that this user receives significantly more total value than the other user, violating both envy-freeness and the sharing incentive. 
-
-Theorem 3. The sharing incentive and Pareto efficiency are incompatible for demand-based systems which deal with time-varying demands of varying importance.
-
-Proof: %XXX, Insert proof, it's super straightforward]
-\subsection{Virtues of economic scheduling}
+\end{itemize}
+
+The results above hold only for demand-based policies.
+The following result shows that the strong guarantees of the sharing
+incentive and Pareto efficiency are actually incompatible in general.
+This motivates us to introduce weaker notions in the next section.
+\begin{theorem}\label{no-efficiency}
+%XXX change the appearance of "theorem 3" below to reference this one
+The sharing incentive and Pareto efficiency are incompatible under realistic conditions.
+\end{theorem}
+\begin{pproof}
+Consider a setting in which there are two phases and two users. 
+The second phase differs from the first in one of two ways: 
+either it is the case that user 2 cares more about their tasks in phase 2 than about their tasks in phase 1, 
+or it is the case that user 1 cares more about their tasks in phase 2 than about their tasks in phase 1. 
+By “cares more about” we mean simply that a user would, all else equal, 
+prefer to complete those tasks more rapidly at the expense of completing other tasks less rapidly.
+
+If user $i$ values jobs more in phase 2, it is easy to verify that any allocation which is both Pareto efficient and compatible with the sharing incentive must give user $i$ 
+more resources than user $j$ in phase 2 and (consequently) fewer resources than user $j$ in phase 1. 
+Since the scheduler must decide which user to give more resources in phase 1, it cannot possibly be Pareto efficient and compatible with the sharing incentive in both cases.
+\end{pproof}
+
+\subsection{Analysis of our policy}
 In this section, we show that our system possesses weaker versions of the theoretical guarantees of the theoretical properties that have been ascribed to existing schedulers.
@@
 
-The first theorem considers the setting in which user's willingness to pay [XXX continue]
-
-Theorem 4.
-[Sharing incentive] Each user A values the total resources they receive at least as much as they value their share of the cluster (i.e.
-the amount paid by A divided by the entire cost paid by all users of the cluster).
-
-Proof: Consider a particular user A. During any auction, let $p_A$ be the price that $A$ pays, 
-let $p_B$ be the price paid by all other users, let $R_A$ be the resources received by A, and let $R_B$ be the resources received by all other users.
-The key point is that user A values $R_A$ at at least $p_A$, and values $R_B$ at at most $p_B$.
-Thus user A values their share of the resources at at least $\frac {p_A}{p_A + p_B}$.
-
-%XXX finish proof, very easy.
-
-Theorem 5.
-Using a closed currency, if the rate of income of a particular user is p, that user can adopt a bidding strategy which ensures that they receive a p fraction of the cluster during any period of length T, where T is an upper bound for the length of a task (i.e.
-the maximum of the minimum amount of time after which any task can be revoked).
-
-Proof:
+We define a user’s fair share of the cluster to be a proportional share of each resource, with the proportion determined by the ratio between the total amount paid by that user, and the amount paid by all users over the cluster.
+
+\begin{theorem}[Sharing incentive]
+Over the life of the cluster, each user A values the total resources they receive at least as much as they value their fair share of the cluster. 
+\end{theorem}
+
+Note that users may value resources at different times differently, and this is a statement across the entire lifetime of the cluster.
+\begin{pproof}
+Consider a particular user A. 
+During any auction, let $p_A$ be the price that A pays, let $p_{-A}$ be the price paid by all other users, let $R_A$ be the resources received by A, 
+and let $R_{-A}$ be the resources received by all other users. The key point is that user A values $R_A$ at at least $p_A$, and values $R_{-A}$ at at most $p_{-A}$.
+
+Summing over all rounds of the auction, A values the total resources they receive at at least the amount they pay for them, 
+and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately.
+\end{pproof}
+
+We need to change the notion of envy-freeness slightly to be appropriate for our setting: 
+because we allow users to bid on resources, it may be that one user consistently pays more than another and therefore receives more resources. 
+So we merely ask that no user envy the allocation of anyone who paid no more than they did.
+
+%XXX link this into the general discussion
+As with the envy-free analysis of DRF, we need to assume that either there are no complementarities between resources, or that the user’s demand for a resource takes into account their expectations about future allocations (e.g.
+if resources R and Q are only valuable together, we either assume that the scheduler packages them together into a single resource or that the frameworks are able to evaluate the value of r based on the probability that they will be able to receive Q).
+
+\begin{theorem}[Local envy-freeness]
+No user who bids honestly would prefer the allocation of another user who paid no more than they did.
+\end{theorem}
+
+\begin{pproof}
+We will show by induction that for any number of rounds, user A would prefer to have received user A’s allocation at user A’s price than user B’s allocation at user B’s price.
+Consider a particular round, after which user A receives some resources $R_A$ at a price $p_A$ and user B receives resources $R_B$ at a price $p_B$.
+
+By the definition of our auction, the price $p_B$ exceeds user A’s willingness to pay for resources $R_B$ (or else user A’s proxy would have continued bidding and the auction would not have concluded), while the price $p_A$ is less than user A’s willingness to pay for resources $R_A$ (or else user A’s proxy would have stopped bidding earlier).
+In particular, user A prefers their package to user B’s package.
+Since at the start of the round user A preferred their allocation at their price to user B’s allocation at user B’s price, this property also holds at the end of the round.
+In this step we rely on our assumption that user A’s valuations for their own holdings do not change after the auction is announced (otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction).
+We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting.
+[]
+\end{pproof}
+
+%XXX insert discussion of strategy-proofness of DRF, which mentions (1) the fact that you need to ignore complexities of items / trust users to incorporate them into their bids, (2) the fact that you need to ignore the consequences of your behavior for other participants
+
+\begin{theorem}[Local strategy-proofness] 
+Assuming that users are indifferent to changes in each others’ budgets,
+and that users’ willingness to pay 
+incorporates accurate expectations of effects on future allocations, 
+the optimal behavior in our auction is to honestly declare willingness to pay.
+\end{theorem}
+
+\begin{pproof}
+We give the standard argument for the dominant strategy truthfulness (strategy-proofness) of Vickrey auctions. 
+Indeed, suppose on the contrary 
+that $$B_1$$ and $B_2$ are two different bids for user A; that $R_1$ and $R_2$ are the resources received after making either of these bids and $p_1$, $p_2$ are the associated prices; that $B_1$ is an honest bid; and that user A prefers $(R_2, p_2)$ to $(R_1, p_1)$.
+
+The defining characteristic of our auction is that $p_i$ is equal to the loss in other participants’ welfare which results from awarding user A the resource bundle $R_i$. 
+WLOG suppose that $p_2> p_1$.
+This means that the auctioneer would need to reduce the prices charged to the other users by at most $(p_2 - p_1)$ in order to change user A’s bundle from $R_1$ to $R_2$. 
+But by hypothesis, user A would be willing to pay more than $(p_2 - p_1)$ in order to make this change. 
+Since $B_1$ was an honest bid, the auctioneer can raise A’s price by more than $(p_2 - p_1)$, 
+and since the auctioneer continues to make favorable modifications until no more are available, it will do so.
+
+This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. 
+\end{pproof}
+
+We must also weaken the notion of Pareto efficiency in order for it to be achievable (see Theorem 3)
+
+%XXX make notes about approximations, say we are analyzing the intractable optimization and that statements hold with appropriate caveats, e.g.
+you aren’t Pareto efficient if you can’t do the optimization exactly, but you are as Pareto efficient as you can realistically be.
+Since optimization is computationally hard, the only way we can avoid this caveat is by ignoring it.]
+%XXX make notes about the notion of ``local'' guarantees
+
+\begin{theorem}[Local Pareto efficiency.]
+If users bid honestly, 
+there is no way to change the tasks which are scheduled at a single time $T$ in a way which makes every user better off.
+\end{theorem}
+
+\begin{pproof}
+At each individual time $T$, the allocation selected is chosen precisely to maximize welfare using the stated preferences of bidders. 
+Consequently, assuming that bidders honestly report their welfare, the allocation which is selected maximizes welfare.
+\end{pproof}
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{images/util_high.png}
+%\includegraphics[width=0.5\textwidth]{images/util_high.png}
 \caption{Utilization achieved by DRF and our policy on a simulated 25-node CPU-bound cluster.  DRF's average utilization is 98\% average utilization while ours is 99\%.}
@@
 
-\includegraphics[width=0.5\textwidth]{images/util_low.png}
+%\includegraphics[width=0.5\textwidth]{images/util_low.png}
 \caption{Behavior of DRF and our policy on a simulated 100-node cluster. Both policies have average utilization of 44\%.}
@@
 
-\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
+%\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
 \caption{Relative average job completion times between DRF and auctions for all frameworks.}
@@
 In the absence of this information, our scheme provides a default bidding policy.
-This ``backwards-compatible" mode must still perform comparable with DRF, especially given the current state of job requests.
+This ``backwards-compatible'' mode must still perform comparable with DRF, especially given the current state of job requests.
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{images/inhomo_times.png}
+%\includegraphics[width=0.5\textwidth]{images/inhomo_times.png}
 \caption{The results of simulating Mesos on a cluster of 64 machines, of which 16 have access to a special resource.

### 2013-12-18 mesos.hpp

@@ -33,6 +33,8 @@ struct Job : public Indexable {
   double start_time;
   double end_time;
 
+  size_t framework_id;
+
 #if 0
   unordered_set<size_t> tasks;
   // Jobs which have to complete before this job can start.

### 2013-12-18 mesosSim.cpp

@@ -182,7 +182,8 @@ void trace_workload(
     }
   }
 
-  allJobs.add(0); // Dummy job with 0 tasks so that real jobs begin at ID 1.
+  Job* job = &allJobs.add(0);
+  job->framework_id = -1; // Dummy job with 0 tasks so that real jobs begin at ID 1.
 
   unordered_map<size_t, double> framework_join_time;
 
@@ -244,6 +245,7 @@ void trace_workload(
       last_j_id = split_v[0];
       // Create a new job since we haven't seen this job yet.
       job = &allJobs.add(0);
+      job->framework_id = framework.id();
       CHECK_EQ(job->id(), last_j_id);
     } else {
       job = &allJobs.get(last_j_id);
@@ -353,6 +355,11 @@ void MesosSimulation::start_task(
     Task& task, double now, double rent) {
 
     output << this->get_clock() << " " << task.id()<< " StartTask" << endl; 
+
+    Job* job = &allJobs.get(task.job_id);
+    if (job->start_time < 0){
+        job->start_time = now;
+    }
 
     Slave& slave = allSlaves.get(slave_id);
     task.slave_id = slave_id;
@@ -496,6 +503,9 @@ void MesosSimulation::log_utilization() {
       << total_resources.cpus << " " << used_resources.mem << " "
       << total_resources.mem << " " << used_resources.disk << " "
       << total_resources.disk << endl;
+      for (auto &f : allFrameworks){
+          cout << "SHARE " << f.id() << " " << f.cpu_share  <<" "<<f.mem_share << endl;
+      }
       LOG(INFO) << "FASTHUNGRY " << gg;
       LOG(INFO) << "FASTSTABLE " << gb;
       LOG(INFO) << "SLOWSTABLE " << bb;
@@ -782,7 +792,7 @@ int main(int argc, char* argv[]) {
   //METRICS: Completion time
   cerr << "#JOB COMPLETION TIMES" << endl;
   for (int i = 0; i < sim.allJobs.size(); ++i) {
-    cerr << i << " " << sim.allJobs[i].end_time << endl;
+    cerr << i << " "<<  sim.allJobs[i].num_total_tasks << " " << sim.allJobs[i].framework_id << " " << sim.allJobs[i].end_time - sim.allJobs[i].start_time << endl;
   }
   //if(DEBUG) cout << "Average job completition time is " <<
   //float(sum)/float(jobs_to_tasks.size()) << endl;

### 2013-12-18 paper/paper.tex
Made table

@@
 
-We will use the suggestive term “realistic conditions” to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
+We will use the suggestive term ``realistic conditions'' to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
 
@@
 
-We say that a system is “demand-based” if it elicits a demand from each user and makes assignments on the basis of the stated demands.
+We say that a system is ``demand-based'' if it elicits a demand from each user and makes assignments on the basis of the stated demands.
 For example, DRF, asset allocation, and CEEI all fall into this class.
@@
 
-Suppose that there are two users and that at each time each user has enough tasks to consume all of the clusters’ resources.
+Suppose that there are two users and that at each time each user has enough tasks to consume all of the clusters' resources.
 Tasks arrive at multiples of time T and last for T rounds.
-Moreover, suppose that during each interval of time T each user has an independently and uniformly randomly generated priority which is either “high” or “low.” The only characteristic of these priorities is that, all else equal, they would prefer run one extra high priority task at the expense of one fewer low priority task.
-
-Since the scheduler is demand-based and the user’s priority levels are changing across time, the allocation must be independent of the priority of the users.
-So if each user receives a non-zero share of the resources, then each user must receive a non-zero share of the resources while they are in the “high” priority state and the other user is in the “low” priority state.
+Moreover, suppose that during each interval of time T each user has an independently and uniformly randomly generated priority which is either ``high'' or ``low.'' The only characteristic of these priorities is that, all else equal, they would prefer run one extra high priority task at the expense of one fewer low priority task.
+
+Since the scheduler is demand-based and the user's priority levels are changing across time, the allocation must be independent of the priority of the users.
+So if each user receives a non-zero share of the resources, then each user must receive a non-zero share of the resources while they are in the ``high'' priority state and the other user is in the ``low'' priority state.
 
@@
 DRF satisfies a weaker form of strategy-proofness which we call ``local strategy-proofness,'' 
-such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler’s future behavior. 
+such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler's future behavior. 
 This differs from the ordinary notion in that a user may need to reason strategically about future rounds of allocation in order to determine
@@
 \begin{itemize}
-\item \textbf{Strategy-proofness:} consider the setting where a framework’s top priority is achieving some particularly valuable resource X 
+\item \textbf{Strategy-proofness:} consider the setting where a framework's top priority is achieving some particularly valuable resource X 
 which is currently in use, though they have other tasks which they value less. To be most extreme, suppose the user values any outcome in which they receive X 
@@
 or it is the case that user 1 cares more about their tasks in phase 2 than about their tasks in phase 1. 
-By “cares more about” we mean simply that a user would, all else equal, 
+By ``cares more about'' we mean simply that a user would, all else equal, 
 prefer to complete those tasks more rapidly at the expense of completing other tasks less rapidly.
@@
 
-We define a user’s fair share of the cluster to be a proportional share of each resource, with the proportion determined by the ratio between the total amount paid by that user, and the amount paid by all users over the cluster.
+We define a user's fair share of the cluster to be a proportional share of each resource, with the proportion determined by the ratio between the total amount paid by that user, and the amount paid by all users over the cluster.
 
@@
 %XXX link this into the general discussion
-As with the envy-free analysis of DRF, we need to assume that either there are no complementarities between resources, or that the user’s demand for a resource takes into account their expectations about future allocations (e.g.
+As with the envy-free analysis of DRF, we need to assume that either there are no complementarities between resources, or that the user's demand for a resource takes into account their expectations about future allocations (e.g.
 if resources R and Q are only valuable together, we either assume that the scheduler packages them together into a single resource or that the frameworks are able to evaluate the value of r based on the probability that they will be able to receive Q).
@@
 \begin{pproof}
-We will show by induction that for any number of rounds, user A would prefer to have received user A’s allocation at user A’s price than user B’s allocation at user B’s price.
+We will show by induction that for any number of rounds, user A would prefer to have received user A's allocation at user A's price than user B's allocation at user B's price.
 Consider a particular round, after which user A receives some resources $R_A$ at a price $p_A$ and user B receives resources $R_B$ at a price $p_B$.
 
-By the definition of our auction, the price $p_B$ exceeds user A’s willingness to pay for resources $R_B$ (or else user A’s proxy would have continued bidding and the auction would not have concluded), while the price $p_A$ is less than user A’s willingness to pay for resources $R_A$ (or else user A’s proxy would have stopped bidding earlier).
-In particular, user A prefers their package to user B’s package.
-Since at the start of the round user A preferred their allocation at their price to user B’s allocation at user B’s price, this property also holds at the end of the round.
-In this step we rely on our assumption that user A’s valuations for their own holdings do not change after the auction is announced (otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction).
+By the definition of our auction, the price $p_B$ exceeds user A's willingness to pay for resources $R_B$ (or else user A's proxy would have continued bidding and the auction would not have concluded), while the price $p_A$ is less than user A's willingness to pay for resources $R_A$ (or else user A's proxy would have stopped bidding earlier).
+In particular, user A prefers their package to user B's package.
+Since at the start of the round user A preferred their allocation at their price to user B's allocation at user B's price, this property also holds at the end of the round.
+In this step we rely on our assumption that user A's valuations for their own holdings do not change after the auction is announced (otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction).
 We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting.
@@
 \begin{theorem}[Local strategy-proofness] 
-Assuming that users are indifferent to changes in each others’ budgets,
-and that users’ willingness to pay 
+Assuming that users are indifferent to changes in each others' budgets,
+and that users' willingness to pay 
 incorporates accurate expectations of effects on future allocations, 
@@
 
-The defining characteristic of our auction is that $p_i$ is equal to the loss in other participants’ welfare which results from awarding user A the resource bundle $R_i$. 
+The defining characteristic of our auction is that $p_i$ is equal to the loss in other participants' welfare which results from awarding user A the resource bundle $R_i$. 
 WLOG suppose that $p_2> p_1$.
-This means that the auctioneer would need to reduce the prices charged to the other users by at most $(p_2 - p_1)$ in order to change user A’s bundle from $R_1$ to $R_2$. 
+This means that the auctioneer would need to reduce the prices charged to the other users by at most $(p_2 - p_1)$ in order to change user A's bundle from $R_1$ to $R_2$. 
 But by hypothesis, user A would be willing to pay more than $(p_2 - p_1)$ in order to make this change. 
-Since $B_1$ was an honest bid, the auctioneer can raise A’s price by more than $(p_2 - p_1)$, 
+Since $B_1$ was an honest bid, the auctioneer can raise A's price by more than $(p_2 - p_1)$, 
 and since the auctioneer continues to make favorable modifications until no more are available, it will do so.
@@
 %XXX make notes about approximations, say we are analyzing the intractable optimization and that statements hold with appropriate caveats, e.g.
-you aren’t Pareto efficient if you can’t do the optimization exactly, but you are as Pareto efficient as you can realistically be.
+you aren't Pareto efficient if you can't do the optimization exactly, but you are as Pareto efficient as you can realistically be.
 Since optimization is computationally hard, the only way we can avoid this caveat is by ignoring it.]
@@
     \hline
-    Desired & \small DRF & \small DRF & \small Market-based  & something & something\\
-    Properties & \small(simple) & \small (complex) & \small Mechanism  & something & something\\
+    Desired & \small DRF & \small DRF & \small Market-based  \\
+    Properties & \small(simple) & \small (realistic) & \small Mechanism \\
     \hline
-    \small Envy-Freeness & \cmark & \cmark  & \cmark & \cmark   & \cmark\\
-    \small Pareto-Efficiency & 5 & 6  & 4  & \cmark  & \cmark\\
-    \small Resource Monotonicity & 8 & 9  & 4  & \cmark  & \cmark \\
-    7 & 8 & 9  & 4  & \cmark  & \cmark \\
-    7 & 8 & 9  & 4  & \cmark  & \cmark\\
-    7 & 8 & 9  & 4 & \cmark  & \cmark\\
+    \small Envy-Free & \cmark &  & \cmark \\
+    \small Pareto-Efficient & \cmark & Locally & Locally  \\
+    \small Strategy-proof & \cmark & Locally  & Locally \\
+    \small Sharing incentive & \cmark &  & \cmark\\
     \hline

### 2013-12-18 paper/paper.tex
Edited abstract and table

@@
 \begin{abstract}
-Current cluster managers arbitrate complex and possibly conflicting user requirements through a fairness criterion such as dominant resource fairness.
-However, in realistic settings, these approaches fail to be both efficient and non-manipulable.
-In this paper, we propose using prices as a method of expressing user constraints, and describe a market-based mechanism for allocating resources in a cluster.
-We demonstrate that our approach achieves desirable theoretical properties, such as envy-freeness and compatibility with sharing incentives.
-We incorporate our mechanism into the design of the Mesos cluster scheduler, and show through simulations that our modifications result in comparable or better performance characteristics when compared with the existing Mesos framework.
-In particular, our scheme can match Mesos's dominant resource fairness's performance when even no economic information is provided.
-When economic information is provided, our mechanism provides performance improvements.
+Existing cluster managers typically allocate resources
+based on a fairness criterion such as dominant resource fairness. 
+However, this approach makes it difficult to accomodate complex requirements
+without substantially increasing the complexity of the scheduler itself.
+Standard approaches to this challenge compromise the efficiency
+and fairness guarantees that make these simple scheduling policies attractive.
+
+In this paper, we propose using prices as a simple and modular
+method of expressing constraints and objectives,
+and describe a microeconomic mechanism for allocating resources
+in a cluster
+We demonstrate that, in contrast with existing techniques,
+our approach maintains its theoretical guarantees even in the presence
+of complex scheduling constraints which are unknown to the scheduler.
+We incorporate our mechanism into the design of the Mesos cluster scheduler, 
+and show through simulations that our modifications result in comparable performance characteristics
+to DRF in simple situations, while achieving improved performance
+in a setting with inhomogeneous resources.
 \end{abstract}
@@
 
-Theoretical analysis
-Drawbacks of non-economic scheduling
+\subsection{Drawbacks of non-economic scheduling}\label{drawbacks}
 Most scheduling policies used in practice do not use any economic information: clients request resources, and schedulers allocate those resources.
@@
 \item \textbf{Envy-freeness and compatibility with sharing incentive:} Suppose that one user consumes $\frac 13$ of the resources in the cluster and another consumes $\frac 12$ of the resources, 
-but a particular $frac 1{10}$ of the resources in the cluster are $10$ times more valuable (to every user) than they appear. 
+but a particular $\frac 1{10}$ of the resources in the cluster are $10$ times more valuable (to every user) than they appear. 
 This could be based on hardware characteristics to which the scheduler is oblivious. 
@@
 
-By the definition of our auction, the price $p_B$ exceeds user A's willingness to pay for resources $R_B$ (or else user A's proxy would have continued bidding and the auction would not have concluded), while the price $p_A$ is less than user A's willingness to pay for resources $R_A$ (or else user A's proxy would have stopped bidding earlier).
+By the definition of our auction, the price $p_B$ exceeds user A's willingness to pay for resources $R_B$ 
+(or else user A's proxy would have continued bidding and the auction would not have concluded), 
+while the price $p_A$ is less than user A's willingness to pay for resources $R_A$ 
+(or else user A's proxy would have stopped bidding earlier). 
 In particular, user A prefers their package to user B's package. 
-Since at the start of the round user A preferred their allocation at their price to user B's allocation at user B's price, this property also holds at the end of the round.
-In this step we rely on our assumption that user A's valuations for their own holdings do not change after the auction is announced (otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction).
-We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting.
-[]
+Since at the start of the round user A preferred their allocation at their price to user B's allocation at user B's price, 
+this property also holds at the end of the round. 
+In this step we rely on our assumption that user A's valuations for their own holdings do not change after the auction is announced 
+(otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction). 
+We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting,
+even in a simple rather than realistic enviornment.
+\qed
 \end{pproof}
@@
 
-\begin{table*}[t!]
-\begin{center}
+\begin{table}[t!]
+%\begin{center}
     \begin{tabular}{| l | l | l | l | l | l |}
@@
     \hline
-    \small Envy-Free & \cmark &  & \cmark \\
+    \small Envy-Free & \cmark &  & Locally \\
     \small Pareto-Efficient & \cmark & Locally & Locally  \\
@@
     \end{tabular}
-\end{center}
-  \caption{A simple table}
+%\end{center}
+  \caption{Properties of DRF in a simple environment
+ compared with properties of DRF and our economic mechanism
+ in a more realistic environment (see section~\ref{drawbacks}).}
   \label{table:props}
-\end{table*}
+\end{table}
 

### 2013-12-18 paper/paper.tex
worked on intro, added images back

@@
 
-Large-scale computing clusters offer potential for greater efficiency through
+Large-scale computing clusters offer the potential for greater efficiency through
 pooling of computational resources, but must contend with the problem of
@@
 realistic settings --- when dealing with inhomogeneous resources, time-varying
-demands, requirements for data locality, etc.---these systems cease to be either
+demands or deadlines, requirements for data locality, etc.---typical implementations
+of these systems cease to be either
 efficient or non-manipulable.
 
-We propose using prices as an abstraction for subsystems to communicate their
-constraints, and describe a protocol based on auctions for allocating resources
-in a cluster. Our protocol has the key advantage that it can continue to meet
+We propose allowing users of the cluster to bid on resources
+as a method of expressing their constraints and priorities without exposing
+those constraints directly to the scheduler. We imagine that the users
+of the cluster will often themselves be programs running on the cluster
+and making choices about bidding programmatically, and stress that we are
+investigating the suitability of this approach as a communication abstraction
+between programs rather than as a user interface to expose to the end-users
+of a computing cluster.
+
+Our protocol has the key advantage that it can continue to meet
 efficiency guarantees in realistic environments where preferences are
-inhomogeneous across resources and time, and in the presence of adversarial
-manipulation. Moreover, we propose prices as a general mechanism for enforcing a
-clean abstraction between different components of a system, allowing one
-component to make choices intelligently based on constraints elsewhere in the
-system even when it was not designed with knowledge of those constraints.
+inhomogeneous across resources and time.
 
@@
 ``agents'' which allow traditional Mesos clients to interact seamlessly with our
-modified implementation.
-We show through simulations that our market-based mechanism has performance characteristics similar or better compared to existing approaches (in particular, DRF) even when users do not
-provide any meaningful price information. Moreover, we show that when accurate
-economic data is available our system is able to achieve substantial
-performance improvements over DRF. Finally, we discuss a number of examples where this
-functionality may be useful even in applications where the end-users of the
-system don't have to think about economics at all, and instead prices are
-generated algorithmically as a principled way to accommodate constraints that
-are currently managed in an ad hoc way.
+modified implementation. We show through simulations that our market-based mechanism 
+achieves comparable performance with the existing implementation of Mesos.
+We then give an example of modifying the bidding behavior of frameworks
+in order to express varying preferences for particular machines in the cluster,
+and show that this modification is able to improve the performance of Mesos.
 
@@
 which are currently using the least resources, Mesos attempts to ensure that all
-frameworks receive a fair share of the cluster. Because of the simplicity of
-this protocol, it appears to be immune to manipulation (and indeed it has been
-shown to be immune to manipulation in theory).
+frameworks receive a fair share of the cluster.
 
@@
 strategy-proof in a simple one-shot game with homogeneous resources, it is
-neither efficient nor strategy-proof in this setting. 
+neither efficient nor strategy-proof in this more realistic setting. 
 %For example, a framework
@@
 Moreover, the
-current design of Mesos is essentially unsuitable for even mildly hostile
+current design of Mesos is essentially unsuitable for hostile
 environments. Section \ref{sec:theory} provides detailed theoretical analyses.
@@
 
-\subsection{Why microeconomic methods?}
-The basic paradigm we propose is conceptually simple, though is associated with
-many practical difficulties. At each stage where we need to make a decision, we
-propose:
-\vspace{-5mm}
-\begin{enumerate}
-\itemsep0em
-  \item Estimate the value of different outcomes.
-  \item Estimate the outcomes that will result from different decisions.
-  \item Compute the value of different decisions.
-\end{enumerate}
-\vspace{-5mm}  
-This paradigm has the virtue of being modular in a number of important respects:
-\vspace{-5mm}
-\begin{enumerate}
-\itemsep0em
-  \item The notion of value provides a unifying framework for different
-    components to communicate with each other; if I am one component providing a
-    service to some client, and I know how valuable different outcomes are to my
-    client, I know everything I need to know; my policy does not need to depend
-    on anything else about the client.
-  \item I can improve and reason about the prediction of outcomes and the
-    estimates of value separately. 
-  \item It is often possible to compute the value straightforwardly, given the
-    values stated  by my clients. For example, if I am scheduling a MapReduce
-    instance and know that a 1 second delay costs my client 1 unit, then I can
-    estimate the cost of a 1 second delay in one of my tasks simply by
-    estimating (or using a crude heuristic for) the probability that this task
-    is on the critical path.
-\end{enumerate}
-
-\section{Market-based Mechanism Design}
+\section{Our auction}
 
@@
 we allow a framework to incur a negative income and also a small temporary negative balance, although we do not accept bids from a framework with a negative balance.
+
+Depending on the setting, the budgets of the frameworks may be entirely internal to the cluster
+using an idiosyncratic currency,
+or the budgets might be shared between several different components of a larger system
+(or frameworks may even draw from real budgets of organizations, individuals, or teams,
+which have significance outside of the cluster).
+The auction we describe is applicable in any of these environments,
+though our evaluations all rely exclusively on a closed economy with an idiosyncratic currency.
 
@@
 \begin{figure}
-%\includegraphics[width=0.5\textwidth]{images/util_high.png}
+\includegraphics[width=0.5\textwidth]{images/util_high.png}
 \caption{Utilization achieved by DRF and our policy on a simulated 25-node CPU-bound cluster.  DRF's average utilization is 98\% average utilization while ours is 99\%.}
@@
 
-%\includegraphics[width=0.5\textwidth]{images/util_low.png}
+\includegraphics[width=0.5\textwidth]{images/util_low.png}
 \caption{Behavior of DRF and our policy on a simulated 100-node cluster. Both policies have average utilization of 44\%.}
@@
 
-%\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
+\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
 \caption{Relative average job completion times between DRF and auctions for all frameworks.}
@@
 \begin{figure}
-%\includegraphics[width=0.5\textwidth]{images/inhomo_times.png}
+\includegraphics[width=0.5\textwidth]{images/inhomo_times.png}
 \caption{The results of simulating Mesos on a cluster of 64 machines, of which 16 have access to a special resource.

### 2013-12-18 paper/paper.tex
Changed section on our proposal

@@
 bids, which we can consider a function of the form
-\[ \mathcal{B}: \mathbf{T}^n \rightarrow \mathbf{R}. \]
-where there are $n$ slaves, $\mathbf{T}$ is a task (containing an amount of desired
-resources on a single slave) and $\mathbf{R}$ is the willingness to pay for the
-list of tasks $\mathbf{T}^n$.
+\[ \mathcal{B}: \Pi_{i=1}^n R_i \rightarrow \mathbf{R}. \]
+where $n$ is the number of slaves, 
+$R_i$ is the space of possible resource assignments on slave $i$,
+and the value $\mathcal{B}\left(R_1, R_2, \ldots, R_n\right)$ is the framework's
+willingness to pay in order to receive resources $R_i$ on slave $i$ for each $i$.
 
 A naive representation of this function would use an exponential amount of
-space, given that each of the $n$ values in $\mathbf{T}^n$ can vary
-independently. While we can consider several methods greatly varying in
+space. While we can consider several methods greatly varying in
 complexity for encoding this function more compactly, we use the following
@@
 \begin{itemize}
-  \item A list of \emph{task packages}, with the assumption that the willingness
-    to pay for any subset of the list is simply the sum of the willingness to
-    pay for each element in the subset
-  \item A list of tasks in each task package, with a specific slave and a
-    willingness to pay for each task. The auction assumes that the framework
-    desires only one of the tasks and values all of them equally.
+  \item A list of \emph{tasks}, with the assumption that a framework's
+    willingness to pay for any set of tasks is simply the total
+    willingness to pay for tasks in that set.
+  \item For each task a list of possible resources which can be used to perform
+    that task, together with a willingness to pay for that set of resources.
 \end{itemize}
 While this obviously cannot represent all possible $\mathcal{B}$, it still
-allows enough flexibility to, e.g., pay more to have a task run on a faster
-machine than a slower one.
+allows enough flexibility to cover all of the applications we allude to
+in the paper---to handle dealdines, inhomogeneous resources, fragmentation,
+tasks of differing priorities, and so on.
 
@@
 
-\paragraph{Paying more or less} To modify the 
+\paragraph{Adjusting bids} To modify the 
 default policy to accomodate inhomogeneous resources,

### 2013-12-18 paper/paper.tex
Changed intro sections further.

@@
 neither efficient nor strategy-proof in this more realistic setting. 
-%For example, a framework
-%using Mesos which prefers to run tasks on machines that already have relevant
-%data is forced to engage in strategic behavior: given a resource which it
-%\emph{could} use now, should it take the resource or decline it, so that it
-%might receive a better offer in the future? Solutions to this problem rely on
-%simple heuristics which require tuning based on the parameters of the system;
-%there are simple examples where the resulting allocations are not efficient
-%despite best-efforts of the clients, and in complex examples there is little to
-%believe the results are efficient. 
+For example, a framework
+using Mesos which prefers to run tasks on machines that already have relevant
+data is forced to engage in strategic behavior: given a resource which it
+\emph{could} use now, should it take the resource or decline it, so that it
+might receive a better offer in the future? Solutions to this problem rely on
+simple heuristics which require tuning based on the parameters of the system;
+there are simple examples where the resulting allocations are not efficient
+despite best-efforts of the clients, and in complex examples there is little to
+believe the results are efficient. 
 Moreover, the
 current design of Mesos is essentially unsuitable for hostile
-environments. Section \ref{sec:theory} provides detailed theoretical analyses.
-%; a framework which can use less than its ``fair share'' of the
-%resources at any point in time has no incentive to do so, and indeed has every
-%incentive to exploit all resources it can be allocated even if they are being
-%used arbitrarily inefficiently (and there is always \emph{something} to do with
-%idle resources, if only perform proof-of-work in exchange for small amounts of
-%money).
+environments. 
+For example,
+a framework which can use less than its ``fair share'' of the
+resources at any point in time has no incentive to do so, and indeed has every
+incentive to exploit all resources it can be allocated even if they are being
+used arbitrarily inefficiently (and there is always \emph{something} to do with
+idle resources, if only perform proof-of-work in exchange for small amounts of
+money).
+Our economic mechanisms are designed to partially remedy these problems.
 
@@
 
+\subsection{Motivating examples}
+
+Consider the following typical situations within a cluster:
+\begin{enumerate}
+  \item Some clients have regular throughput and flexible deadlines, while some
+    clients have hard real-time constraints and variable traffic.
+  \item Different tasks make use of different characteristics of hardware on
+    machines in the cluster, for example high ratios of RAM to CPU on a
+    particular machine, or GPUs or other hardware that is available on only
+    certain machines.
+  \item Tasks require data which is located on disk or even in memory somewhere
+    in the cluster, and co-locating the tasks with the data improves
+    performance.
+\end{enumerate}
+
+In section~\ref{drawbacks} we show that current implementations
+of Mesos do not remain efficient, strategy-proof, envy-free,
+or compatible with the sharing incentive under these conditions.
+The key problem is that the accept/reject framework is not sufficiently expressive
+to allow users to ``honestly'' express their preferences in these cases,
+and so it is unsurprising that they are incentivized to engage
+in strategic behavior (indeed, they are intended to engage in strategic behavior)
+and the results need not be efficient.
+
+There have bene many ad hoc proposals to address some of these difficulties.
+For example, Jockey is a system which accomodates deadlines in a fair-share
+scheduler by increasing the allotted shares for users which are appraoching
+a deadline.
+However, these techniques tend to violate the theoretical guarantees
+of the underlying systems more starkly, and to require extensive tuning
+in order to achieve good performance.
+We seek a more general framework for addressing these difficulties.
+
+Similarly, we might cope with the need for pre-emption by using various
+heuristics to minimize the extent of overhead associated with evicting a running
+task.
+These heuristics may work well in practice, but are also likely to require
+tuning and to be sensitive to the exact nature of the cluster.
+
+An approach based on pricing might be able to solve all of these difficulties,
+by expressing the costs associated with missing a deadline or evicting a task 
+(potentially automatically) and then making scheduling decisions to maximize
+social welfare.
+We do not propose such an extensive solution in this paper; instead,
+we make an argument for the general desirability of such an approach and provide
+some extremely preliminary evidence for its feasibility.
+
 %\section{The case for microeconomic scheduling}
@@
 
-\section{Our auction}
+\section{Our allocation policy}
 
@@
 master.
+
+In the case of a single indivisible resource, this corresponds exactly
+to a second-price auction; in general it is quite similar
+to the Vickrey-Clarke-Groves auction, in which the chosen allocation
+maximizes social welfare and each framework is charged a price
+equal to the social welfare opportunity cost of the resources
+that framework requested. In the rest of this section we describe the auction
+itself in more detail.
 

### 2013-12-18 paper/paper.tex
format edits

@@
 task it wishes to run. 
-
+\vspace{-5mm}
 \paragraph{Default policy} For backwards compatibility, 
@@
 than the others would begin winning auctions.
-
+\vspace{-5mm}
 \paragraph{Adjusting bids} To modify the 
@@
 %XXX mention why we don't care about any properties other than those that we mention
-
+\vspace{-5mm}
 \paragraph{Defensive bidding} One negative consequence of using a closed economy,
@@
 For example, DRF, asset allocation, and CEEI all fall into this class.
-
+\vspace{-5mm}
 \begin{theorem}\label{demand-bad}
@@
 \end{theorem}
-
+\vspace{-5mm}
 \begin{pproof}
@@
 \end{pproof}
-
+\vspace{-5mm}
 \begin{theorem}
@@
 \end{theorem}
-
+\vspace{-5mm}
 DRF satisfies a weaker form of strategy-proofness which we call ``local strategy-proofness,'' 
@@
 
-Proof: For variety, we consider the case of inhomogeneous resources.
+\textbf{Proof} For variety, we consider the case of inhomogeneous resources.
 Again, the proof is identical in any of the given cases.
 For each property we construct a special situation in which DRF fails to achieve that property.
-
+\vspace{-5mm}
 \begin{itemize}
+\itemsep0em
 \item \textbf{Strategy-proofness:} consider the setting where a framework's top priority is achieving some particularly valuable resource X 
@@
 This motivates us to introduce weaker notions in the next section.
+\vspace{-5mm}
 \begin{theorem}\label{no-efficiency}
@@
 \end{theorem}
+\vspace{-5mm}
 \begin{pproof}
@@
 more resources than user $j$ in phase 2 and (consequently) fewer resources than user $j$ in phase 1. 
-Since the scheduler must decide which user to give more resources in phase 1, it cannot possibly be Pareto efficient and compatible with the sharing incentive in both cases.
+Since the scheduler must decide which user to give more resources in phase 1, it cannot possibly be Pareto efficient and compatible with the sharing incentive in both cases. \qed
 \end{pproof}
@@
 We define a user's fair share of the cluster to be a proportional share of each resource, with the proportion determined by the ratio between the total amount paid by that user, and the amount paid by all users over the cluster.
-
+\vspace{-5mm}
 \begin{theorem}[Sharing incentive]
@@
 \end{theorem}
-
+\vspace{-5mm}
 Note that users may value resources at different times differently, and this is a statement across the entire lifetime of the cluster.
+\vspace{-5mm}
 \begin{pproof}
@@
 Summing over all rounds of the auction, A values the total resources they receive at at least the amount they pay for them, 
-and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately.
+and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately. \qed
 \end{pproof}
@@
 if resources R and Q are only valuable together, we either assume that the scheduler packages them together into a single resource or that the frameworks are able to evaluate the value of r based on the probability that they will be able to receive Q).
-
+\vspace{-5mm}
 \begin{theorem}[Local envy-freeness]
@@
 \end{pproof}
-
 %XXX insert discussion of strategy-proofness of DRF, which mentions (1) the fact that you need to ignore complexities of items / trust users to incorporate them into their bids, (2) the fact that you need to ignore the consequences of your behavior for other participants
-
+\vspace{-8mm}
 \begin{theorem}[Local strategy-proofness] 
@@
 \end{theorem}
-
+\vspace{-7mm}
 \begin{pproof}
@@
 Indeed, suppose on the contrary 
-that $$B_1$$ and $B_2$ are two different bids for user A; that $R_1$ and $R_2$ are the resources received after making either of these bids and $p_1$, $p_2$ are the associated prices; that $B_1$ is an honest bid; and that user A prefers $(R_2, p_2)$ to $(R_1, p_1)$.
+that $B_1$ and $B_2$ are two different bids for user A; that $R_1$ and $R_2$ are the resources received after making either of these bids and $p_1$, $p_2$ are the associated prices; that $B_1$ is an honest bid; and that user A prefers $(R_2, p_2)$ to $(R_1, p_1)$.
 
@@
 
-This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. 
+This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. \qed 
 \end{pproof}
-
-We must also weaken the notion of Pareto efficiency in order for it to be achievable (see Theorem 3)
-
+\vspace{-5mm}
+We must also weaken the notion of Pareto efficiency in order for it to be achievable (see Theorem 3):
+\vspace{-5mm}
 %XXX make notes about approximations, say we are analyzing the intractable optimization and that statements hold with appropriate caveats, e.g.
@@
 %XXX make notes about the notion of ``local'' guarantees
-
 \begin{theorem}[Local Pareto efficiency.]
@@
 \end{theorem}
-
+\vspace{-5mm}
 \begin{pproof}
 At each individual time $T$, the allocation selected is chosen precisely to maximize welfare using the stated preferences of bidders. 
-Consequently, assuming that bidders honestly report their welfare, the allocation which is selected maximizes welfare.
+Consequently, assuming that bidders honestly report their welfare, the allocation which is selected maximizes welfare. \qed
 \end{pproof}
@@
 We study the performance of DRF and the market-based mechanism both when pricing information is not available and a default bidding policy must be used, and when pricing information is specified under a specific policy.
-These simulations were run under a statistical workload generated from a month-long Google cluster trace \cite{TODO}.
-
-\subsection{Simulation Implementation\\}
-
+These simulations were run under a statistical workload generated from a month-long Google cluster trace \cite{googlecluster}.
+\vspace{-1mm}
+\subsection{Simulation Implementation}
 Our evaluation is conducted through an event-based simulator of Mesos, implemented with both the DRF and the auction-based resource scheduling algorithms.
@@
 
-\subsection{Performance Without Pricing\\}
+\subsection{Performance Without Pricing}
 
@@
 \label{img:util_low}
-\end{figure}
-
-\begin{figure}
-
-\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
-\caption{Relative average job completion times between DRF and auctions for all frameworks.}
-\label{img:relative}
 \end{figure}
@@
 
+\begin{figure}
+
+\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
+\caption{Relative average job completion times between DRF and auctions for all frameworks.}
+\label{img:relative}
+\end{figure}
+
 Finally, Figure \ref{img:relative} displays the relative average job completion time between DRF and the market-based mechanism for the five frameworks.
@@
 
-\subsection{Performance With Pricing\\}
+\subsection{Performance With Pricing}
 
 When pricing information is provided, we show that the market-based mechanism can provide better performance than in DRF.
-As discussed in Section TODO, there are many situations in which prices can be used to better encapsulate a framework's preferences.
 As a case study, we investigate one particular scenario of inhomogeneous performing resources.
@@
 \label{sec:related}
+
+There are a number of related works in the same or similar domains.
 

### 2013-12-18 paper/paper.tex
Spellecheck, more changes.

--- 2013-12-18 paper/paper.tex
@@
 based on a fairness criterion such as dominant resource fairness. 
-However, this approach makes it difficult to accomodate complex requirements
+However, this approach makes it difficult to accommodate complex requirements
 without substantially increasing the complexity of the scheduler itself.
@@
 incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
-criterions, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
+criteria, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
 simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
@@
 
-\subsection{Motivating examples}
+\subsection{Motivating examples}\label{examples}
 
@@
 
-There have bene many ad hoc proposals to address some of these difficulties.
-For example, Jockey is a system which accomodates deadlines in a fair-share
-scheduler by increasing the allotted shares for users which are appraoching
+There have been many ad hoc proposals to address some of these difficulties.
+For example, Jockey is a system which accommodates deadlines in a fair-share
+scheduler by increasing the allotted shares for users which are approaching
 a deadline.
@@
 
-Similarly, we might cope with the need for pre-emption by using various
+Similarly, we might cope with the need for preemption-  by using various
 heuristics to minimize the extent of overhead associated with evicting a running
@@
 allows enough flexibility to cover all of the applications we allude to
-in the paper---to handle dealdines, inhomogeneous resources, fragmentation,
+in the paper---to handle deadlines, inhomogeneous resources, fragmentation,
 tasks of differing priorities, and so on.
@@
 \paragraph{Adjusting bids} To modify the 
-default policy to accomodate inhomogeneous resources,
+default policy to accommodate inhomogeneous resources,
 times, or tasks, we can simply modify framework's
@@
 It can then spend this budget at a future point in order to monopolize the cluster,
-which may have undesirable conseuqences for frameworks that need uninterrupted service.
+which may have undesirable consequences for frameworks that need uninterrupted service.
 
@@
 either the maximum length of a task or the period of time after which the resources used by a task
-will be reauctioned and potentially revoked).
+will be re-auctioned and potentially revoked).
 In fact the second invariant follows from the first, which can be approximately attained
@@
 We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting,
-even in a simple rather than realistic enviornment.
+even in a simple rather than realistic environment.
 \qed
@@
 When pricing information is provided, we show that the market-based mechanism can provide better performance than in DRF.
-As discussed in Section TODO, there are many situations in which prices can be used to better encapsulate a framework's preferences.
+As discussed in Section~\ref{examples}, there are many situations in which prices can be used to better encapsulate a framework's preferences.
 As a case study, we investigate one particular scenario of inhomogeneous performing resources.
@@
 instead operate as a queue for predefined jobs which are run as resources become
-available. Machines and job requirements also tend to show more homogeniety
+available. Machines and job requirements also tend to show more homogeneity
 within such environments (for example, the ratio between CPU, memory, and disk),
-so sthe amount of optimization possible with pricing is lower.
+so the amount of optimization possible with pricing is lower.
 
@@
 their value of gaining resources was too low compared to the others, since the
-user keeps some amont of money unspent as a a result.
+user keeps some amount of money unspent as a a result.
 
@@
 achieving a fair allocation, but also for frameworks to express their
-preferences in a fine-grianed way using prices and willingness to pay.
+preferences in a fine-grained way using prices and willingness to pay.
 
@@
 
-In our evaluation, we showed through simulation the benefits of our protocol in the specific case of inhomogenous performing resources.
+In our evaluation, we showed through simulation the benefits of our protocol in the specific case of inhomogeneous performing resources.
 However, there are a number of other user constraints that should theoretically be better expressed using prices than existing methods.
@@
 
-\section{Acknowledgement}
+\section{Acknowledgment}
 

### 2013-12-18 paper/paper.tex
Typo fix
Typo fixes

--- 2013-12-18 paper/paper.tex
@@
 incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
-criterions, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
+criterion, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
 simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
@@
   \item Understand the entire optimization problem faced by each problem, and
-    make explicit judgments of the relative value of $R$ and $R'$ within the
+    make explicit judgements of the relative value of $R$ and $R'$ within the
     scheduler. This violates the spirit of Mesos, and in general appears to be
@@
 Once the master has collected a set of bids, it uses an ascending-bid clock
-auction to determine which of the bids to fulfill, and how much it should charge
+auction to determine which of the bids to fulfil, and how much it should charge
 for each of the tasks which win the auction. The auction consists of a number of
@@
 \subsection{Grid computing}
-Job schedulers like TORQUE \cite{torque}, Condor \cite{condor}, and LSF
-\cite{lsf} have long been used for solving the problem of resource allocation
+Job schedulers like TORQUE \cite{torque} or Condor \cite{condor} have long been used for solving the problem of resource allocation
 within a high-performance-computing (HPC) or grid-computing environment.
@@
 \subsection{Resource allocation}
-Dominant resource fairness~\cite{drf} is an allocation policy whereby the user with the smallest dominant share is next allocated resources.
-The user's dominant share in a multi-resource environment is the largest share the user possesses of any of the cluster's various resources.
+Dominant resource fairness~\cite{drf} is an allocation policy whereby the user
+with the smallest dominant share is next allocated resources. The user's
+dominant share in a multi-resource environment is the largest share the user
+possesses of any of the cluster's various resources. The Mesos cluster manager
+relies on the DRF policy to decide which framework to next offer resources.
+Section \ref{sec:theory} contains a more theoretical discussion of DRF and 
+its benefits compared to a market-based mechanism.
 

### 2013-12-18 paper/paper.tex

--- 2013-12-18 paper/paper.tex
@@
 achieves comparable performance with the existing implementation of Mesos.
-We then give an example of modifying the bidding behavior of frameworks
+We then give an example of modifying the bidding behavior of users.
 in order to express varying preferences for particular machines in the cluster,
@@
 obtained resources to run \emph{tasks} on the slaves.
+(We will use the expression ``frameworks'' and ``users'' interchangeably,
+depending on the context.)
 
@@
 by an amount depending on the anticipated speedup.
-%XXX mention why we don't care about any properties other than those that we mention
-
+\vspace{-5mm}
 \paragraph{Defensive bidding} One negative consequence of using a closed economy,
 in which the frameworks bid using currency which is entirely internal to the cluster,
-%XXX mention this distinction elsewhere, and the fact that we can do either
 is the possibility of \emph{hoarding}, in which one framework
@@
 
+We are interested in understanding the suitability of auctions
+as a method for allocating resources.
+To this end, it is prudent to compare the theoretical properties of auctions
+with the theoretical properties of alternatives, particularly various fair-share
+schedulers which have been proposed.
+
+The theoretical properties we are most interested are those concerning the welfare
+produced by the system.
+This includes Pareto efficiency, envy-freeness, and the ``sharing incentive''
+(a system offers a sharing incentive if each user prefers the system
+to simply taking their share of the cluster and going home),
+but also the manipulability of our systems
+(since manipulation may interfere with the reliability of the information
+provided by the users, potentially rendering it useless).
+
+One strong theme throughout this analysis will be the definition of ``local'' versions
+of typical guarantees.
+These appear to be necessary if we want to analyze the behavior of any of our systems
+in a realistic environment, and in particualr in dynamic contexts:
+as we show in the next section, it is typically impossible to achieve
+almost any desirable properties in the dynamic setting.
+Instead, we will talk about obtaining properties at each point in time,
+leaving open the possibility of interactions between different points in time
+violating these guarantees.
+We stress that this relaxation is necessary not only for our system,
+but for existing approaches and (in many cases) provably for all systems.
+
 \subsection{Drawbacks of non-economic scheduling}\label{drawbacks}
@@
 \end{theorem}
-
-DRF satisfies a weaker form of strategy-proofness which we call ``local strategy-proofness,'' 
-such that a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler's future behavior. 
+\vspace{-5mm}
+DRF satisfies a weaker form of strategy-proofness which we call ``local strategy-proofness:'' 
+a user is incentivized to honestly state their demands given their beliefs about the effect of those demands on the scheduler's future behavior. 
 This differs from the ordinary notion in that a user may need to reason strategically about future rounds of allocation in order to determine
 their demand, rather than honestly reporting their real demand.
-%XXX replace user by framework
-%XXX fold this into the clearer general discussion of loca guarantees
-
-Proof: For variety, we consider the case of inhomogeneous resources.
-Again, the proof is identical in any of the given cases.
-For each property we construct a special situation in which DRF fails to achieve that property.
-
+
+\textbf{Proof} For variety, we will prove this theorem in the case of inhomogeneous resources. 
+Again, the proof is identical in any of the given cases. For each property we construct a special situation in which DRF fails to achieve that property.
+\vspace{-5mm}
 \begin{itemize}
+\itemsep0em
 \item \textbf{Strategy-proofness:} consider the setting where a framework's top priority is achieving some particularly valuable resource X 
@@
 This motivates us to introduce weaker notions in the next section.
+\vspace{-5mm}
 \begin{theorem}\label{no-efficiency}
-%XXX change the appearance of "theorem 3" below to reference this one
 The sharing incentive and Pareto efficiency are incompatible under realistic conditions.
 \end{theorem}
+\vspace{-5mm}
 \begin{pproof}
@@
 
+Rather than considering our policy directly, we will work with an idealized variant.
+Our policy performs an \emph{approximate} optimization in order to remain scalable (indeed, it is easy to check that the general allocation problem
+is NP-hard);
+in the idealized variant, we instead imagine performing each auction by selecting the \emph{exact} optimum of the scheduling policy.
+Because each individual scheduling problem tends to concern a small fraction of the cluster's resources,
+this is not a stretch from reality (and we can
+
+Naturally, it is much easier to prove guarantees for the exact version: for example, it is NP-hard to be exactly Pareto efficient in realistic
+situations
+even if we know the preferences of every user.
+This is not merely a technical problem; it means that there can be no Pareto efficient computationally tractable schedulers in general.
+So the Pareto efficiency of the exact scheme which we are approximating is the best that we could hope for in general,
+and to the extent that Pareto efficiency is a useful theoretical property this is the version we should establish.
+
 We define a user's fair share of the cluster to be a proportional share of each resource, with the proportion determined by the ratio between the total amount paid by that user, and the amount paid by all users over the cluster.
-
+\vspace{-5mm}
 \begin{theorem}[Sharing incentive]
@@
 Summing over all rounds of the auction, A values the total resources they receive at at least the amount they pay for them, 
-and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately.
+and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately. \qed
 \end{pproof}
+
+Using the same idea, we can establish that if the size of a cluster is increased by a multiple of $(1 + \epsilon)$ and we add a set of (potentially malicious) users whose total
+budget is bounded by $\epsilon$, the resulting allocation is at least as good for every existing user.
+This guarantees that the worst that a malicious or buggy user can do is ``walk away with their share of the cluster.''
 
@@
 
-%XXX link this into the general discussion
 As with the envy-free analysis of DRF, we need to assume that either there are no complementarities between resources, or that the user's demand for a resource takes into account their expectations about future allocations (e.g.
 if resources R and Q are only valuable together, we either assume that the scheduler packages them together into a single resource or that the frameworks are able to evaluate the value of r based on the probability that they will be able to receive Q).
-
+\vspace{-5mm}
 \begin{theorem}[Local envy-freeness]
@@
 \end{pproof}
-
-%XXX insert discussion of strategy-proofness of DRF, which mentions (1) the fact that you need to ignore complexities of items / trust users to incorporate them into their bids, (2) the fact that you need to ignore the consequences of your behavior for other participants
-
+\vspace{-8mm}
+In the case of strategy-proofness we again weaken our target conditions
+to a local condition: we allow users to strategically look-ahead to future
+rounds in order to determine how much they are willing to pay for a particular resource,
+but require that within a single round they must honestly state those preferences.
+We observe that in the dynamic setting DRF is only strategy-proof in the same ``local'' sense
 \begin{theorem}[Local strategy-proofness] 
@@
 
-This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. 
+This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. \qed 
 \end{pproof}
-
-We must also weaken the notion of Pareto efficiency in order for it to be achievable (see Theorem 3)
-
-%XXX make notes about approximations, say we are analyzing the intractable optimization and that statements hold with appropriate caveats, e.g.
-you aren't Pareto efficient if you can't do the optimization exactly, but you are as Pareto efficient as you can realistically be.
-Since optimization is computationally hard, the only way we can avoid this caveat is by ignoring it.]
-%XXX make notes about the notion of ``local'' guarantees
-
+\vspace{-5mm}
+We must also weaken the notion of Pareto efficiency in order for it to be achievable (see Theorem~\ref{no-efficiency})
+\vspace{-5mm}
 \begin{theorem}[Local Pareto efficiency.]
@@
 
-\subsection{Performance With Pricing\\}
+\subsection{Performance With Pricing}
 
 When pricing information is provided, we show that the market-based mechanism can provide better performance than in DRF.
-As discussed in Section~\ref{examples}, there are many situations in which prices can be used to better encapsulate a framework's preferences.
 As a case study, we investigate one particular scenario of inhomogeneous performing resources.

### 2013-12-18 paper/paper.tex

@@
 incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
-criteria, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
+criterion, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
 simplicity, efficiency, and non-manipulability. Unfortunately, when applied in

### 2013-12-18 paper/paper.tex
Fixes

@@
 \subsection{Grid computing}
-Job schedulers like TORQUE \cite{torque} or Condor \cite{condor} have long been used for solving the problem of resource allocation
+Job schedulers like TORQUE \cite{torque}, Condor \cite{condor}, or LFS \cite{LFS} have long been used for solving the problem of resource allocation
 within a high-performance-computing (HPC) or grid-computing environment.
@@
 \subsection{Economics/pricing in computer systems}
-Lottery scheduling
+Lottery scheduling \cite{lottery} is an example of economic principles applied to computer systems.
+In lottery scheduling, processes or users are assigned a number of lottery tickets, and the scheduler draws a random lottery ticket.
+The ticket holder is next scheduled or awarded resources.
+This probabilistic scheduling algorithm solves starvation as each user has a non-zero probability of being selected in each lottery round.
+Lottery tickets can also be distributed non-uniformly to compensate certain users or boost their chance of scheduling.
 

### 2013-12-18 paper/paper.tex
Better image placement
More changes.

@@
 criterion, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
-simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
+simplicity, efficiency, and non manipulability. Unfortunately, when applied in
 realistic settings --- when dealing with inhomogeneous resources, time-varying
@@
 
-\subsection{Microeconomic methods}
 In this paper we confront the challenge of modifying Mesos to provide more
@@
 frameworks are most willing to pay.
-
-We stress the distinction between this use of price signals and the more typical
-motivation. We are most interested in price signals as an \emph{abstraction} which
-programs can use to express their constraints, rather than as a mechanism to
-extract revenue for the cluster operator or to arbitrate between competing
-external interests. To consider a simple case, suppose there are two programs
-that are contending for a shared resource $R$. Each could either make use of $R$ or
-some alternative resource $R'$ (for example, a different machine in the cluster at
-a different time). Our proposal is to have each program articulate the value of
-resource $R$ (compared to the benchmark of not receiving resource $R$, and then
-contending for resource $R'$ at a later date). The primary alternatives that have
-been considered are:
-\vspace{-4mm}
-\begin{enumerate}
-\itemsep0em
-  \item Ignore the relative value of resource $R$ and $R'$, and make allocation
-    decisions entirely on the basis of fairness considerations (for example by
-    ensuring that each framework has an equal number of every resource). This is
-    the approach taken by Mesos, although it in fact achieves better behavior
-    precisely by \emph{violating} the strategy-proofness of its underlying allocation
-    policy, and providing incentives to frameworks to strategically decline a
-    resource in order to receive a better allocation in the future.
-  \item Understand the entire optimization problem faced by each problem, and
-    make explicit judgements of the relative value of $R$ and $R'$ within the
-    scheduler. This violates the spirit of Mesos, and in general appears to be
-    difficult given the complexity and scale of the cluster scheduling problem.
-\end{enumerate}
 
@@
     \hline
-    \small Envy-Free & \cmark &  & Locally \\
-    \small Pareto-Efficient & \cmark & Locally & Locally  \\
+    \small Envy-Free & \cmark &  & Locally\footnote{No framework envies a framework that pays less.} \\
+    \small Pareto-Efficient & \cmark & Locally\footnote{With caveats arising from computational hardness of packing problems.} & Locally\footnote{With caveats arising from computational hardness of packing problems}  \\
     \small Strategy-proof & \cmark & Locally  & Locally \\
@@
 
-\subsection{Performance Without Pricing}
-
-\begin{figure}
+\begin{figure}[ht]
 \includegraphics[width=0.5\textwidth]{images/util_high.png}
@@
 \end{figure}
+
+\subsection{Performance Without Pricing}
 
@@
 
-\begin{figure}
-
-\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
-\caption{Relative average job completion times between DRF and auctions for all frameworks.}
-\label{img:relative}
-\end{figure}
-
 Finally, Figure \ref{img:relative} displays the relative average job completion time between DRF and the market-based mechanism for the five frameworks.
@@
 \subsection{Performance With Pricing}
+
+\begin{figure}
+
+\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
+\caption{Relative average job completion times between DRF and auctions for all frameworks.}
+\label{img:relative}
+\end{figure}
 
@@
 Simulation evaluation shows that our market-based mechanism can perform reasonably in a backwards-compatible mode, where no economic information is provided.
-When economic data exists, our approach can provide substantial performance benefits.
+We also provide theoretical and experimental evidence that our approach can help manage difficulties
+resulting from constraints that are unknown to the scheduler.
 

### 2013-12-18 paper/paper.tex
Misc. changes

@@
 \usepackage{amsmath}
+\usepackage{caption}
 \usepackage{mathtools}
@@
 
-Users have time-varying demands and tasks of varying importance.
-Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
-Users face deadlines.
-Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources.
+\begin{itemize}
+\item Users have time-varying demands and tasks of varying importance.
+\item Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
+\item Users face deadlines.
+\item Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources.
 Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.
+\end{itemize}
 
@@
 Since the scheduler must decide which user to give more resources in phase 1, it cannot possibly be Pareto efficient and compatible with the sharing incentive in both cases. \qed
+\qed
 \end{pproof}
@@
 and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately. \qed
+\qed
 \end{pproof}
@@
 This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. \qed 
+\qed
 \end{pproof}
@@
 Consequently, assuming that bidders honestly report their welfare, the allocation which is selected maximizes welfare. \qed
+\qed
 \end{pproof}
@@
     \hline
-    \small Envy-Free & \cmark &  & Locally\footnote{No framework envies a framework that pays less.} \\
-    \small Pareto-Efficient & \cmark & Locally\footnote{With caveats arising from computational hardness of packing problems.} & Locally\footnote{With caveats arising from computational hardness of packing problems}  \\
+    \small Envy-Free & \cmark &  & Locally* \\
+    \small Pareto-Efficient & \cmark & Locally** & Locally**   \\
     \small Strategy-proof & \cmark & Locally  & Locally \\
@@
  in a more realistic environment (see section~\ref{drawbacks}).}
+\caption*{* No framework envies another framework that pays less.}
+\caption*{** Modulo difficulties resulting from indivisibility of tasks / computational
+hardness of packing problems.}
   \label{table:props}
@@
 
-\section{Acknowledgment}
+\section{Acknowledgments}
 

### 2013-12-18 paper/paper.tex
Space fixes

@@
 Consider the following typical situations within a cluster:
+\vspace{-5mm}
 \begin{enumerate}
+\itemsep0em
   \item Some clients have regular throughput and flexible deadlines, while some
@@
 \end{enumerate}
-
+\vspace{-5mm}
 In section~\ref{drawbacks} we show that current implementations
@@
 two-level representation:
+\vspace{-5mm}
 \begin{itemize}
+\itemsep0em
   \item A list of \emph{tasks}, with the assumption that a framework's
@@
 \end{itemize}
+\vspace{-5mm}
 While this obviously cannot represent all possible $\mathcal{B}$, it still
@@
 We will use the suggestive term ``realistic conditions'' to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
-
+\vspace{-5mm}
 \begin{itemize}
+\itemsep0em
 \item Users have time-varying demands and tasks of varying importance.
@@
 \end{itemize}
-
+\vspace{-5mm}
 We say that a system is ``demand-based'' if it elicits a demand from each user and makes assignments on the basis of the stated demands.
@@
 
-Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences than DRF, resulting in better performance for the market-based mechanism.
+Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences for special resources than DRF, resulting in better performance for the market-based mechanism.
 DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others.
-By better scheduling jobs on machines that best complete them, we see the overall performance improvements of the market-based mechanism.
 

### 2013-12-18 paper/paper.tex
More changes.

@@
 Our policy performs an \emph{approximate} optimization in order to remain scalable (indeed, it is easy to check that the general allocation problem
-is NP-hard);
+is NP-hard, and consequently that there is \emph{no} non-trivial policy that is Pareto efficient);
 in the idealized variant, we instead imagine performing each auction by selecting the \emph{exact} optimum of the scheduling policy.
-Because each individual scheduling problem tends to concern a small fraction of the cluster's resources,
-this is not a stretch from reality (and we can
-
-Naturally, it is much easier to prove guarantees for the exact version: for example, it is NP-hard to be exactly Pareto efficient in realistic
-situations
-even if we know the preferences of every user.
-This is not merely a technical problem; it means that there can be no Pareto efficient computationally tractable schedulers in general.
-So the Pareto efficiency of the exact scheme which we are approximating is the best that we could hope for in general,
-and to the extent that Pareto efficiency is a useful theoretical property this is the version we should establish.
+Naturally, it is much easier to prove guarantees for the exact version: when the scheduling problems are small or are broken up into small pieces,
+this is not a significant distortion. Moreover, we can never hope for anything beyond this kind of approximate
+Pareto efficiency for computational reasons, so this seems to be the theoretical property of most interest.
 
@@
 \end{pproof}
-\vspace{-8mm}
+\vspace{-5mm}
 In the case of strategy-proofness we again weaken our target conditions

### 2013-12-18 paper/paper.tex
Seciton heading floating

--- 2013-12-18 paper/paper.tex
@@
 \newcommand{\cmark}{\ding{51}}%
+
+ \makeatletter
+  \let\@copyrightspace\relax
+   \makeatother
 
@@
 different machines at different times, some may have complex constraints on data
-locality, etc.
+locality, etc. \\
 
@@
 Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences for special resources than DRF, resulting in better performance for the market-based mechanism.
-DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others.
+DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others.\\
 
@@
 We also provide theoretical and experimental evidence that our approach can help manage difficulties
-resulting from constraints that are unknown to the scheduler.
+resulting from constraints that are unknown to the scheduler.\\\\
 
